---
title: "Stands_data"
author: "Zhehan"
date: "February 10, 2020"
output: html_document
---

#Package
```{r}
library(ggplot2)
library(ggsci)
library(dplyr)
library(lubridate)
library(RColorBrewer)
library(wesanderson)
library(tidyr)
library(reshape2)
library(gridExtra)
library(raster)
library(readxl)
```


#Read data
```{r}
path_stands <- "C:/Users/zt92/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/Stands"
gs <- read.csv(file.path(path_stands, "S.STANDS.csv"))

str(gs)
names(gs)

#cleaning
names(gs)[3] <- "TIMESTAMP"
gs$TIMESTAMP <- as.POSIXct(gs$TIMESTAMP, format = "%m/%d/%Y %H:%M")

#calculate reflectance
gs <- gs %>% mutate(R532 = X532OUT/X532IN)
gs <- gs %>% mutate(R570 = X570OUT/X570IN)
gs <- gs %>% mutate(R650 = X650OUT/X650IN)
gs <- gs %>% mutate(R810 = X810OUT/X810IN)
#calculate PRI and NDVI
gs <- gs %>% mutate(PRI = (R532-R570)/(R532+R570))
gs <- gs %>% mutate(NDVI = (R810-R650)/(R810+R650))
#Add date and huor
gs <- gs %>% mutate(Date = lubridate::date(TIMESTAMP))
gs <- gs %>% mutate(Time = lubridate::hour(TIMESTAMP)+minute(TIMESTAMP)/60+second(TIMESTAMP)/3600)
#Add ID 
gs <- gs %>% mutate(ID = paste(BLOCK, TREATMENT, by = " "))
#remove the first and last day 
gs <- subset(gs, Date > "2019-05-07" & Date < "2019-09-05")

```

#Function to select only noon time 
```{r}
noon_selection <- function(data, early, late){
  data_noon <- data[data$Time >= early & data$Time <= late,]
  return(data_noon)
}
date_selection <- function(data, begin, end){
  data_date_selection <- data[data$Date >= begin & data$Date <= end,]
  return(data_date_selection)
}
```

#Dirunal cycle
##Check the incoming radiation 
```{r}
#X532IN
ggplot(subset(gs, Date == "2019-06-01"), aes(x = TIMESTAMP, y = X532IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In532 2019-06-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-07-01"), aes(x = TIMESTAMP, y = X532IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In532 2019-07-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-08-01"), aes(x = TIMESTAMP, y = X532IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In532 2019-08-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-09-01"), aes(x = TIMESTAMP, y = X532IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In532 2019-09-01") + scale_color_d3()

#X570IN
ggplot(subset(gs, Date == "2019-06-01"), aes(x = TIMESTAMP, y = X570IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In570 2019-06-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-07-01"), aes(x = TIMESTAMP, y = X570IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In570 2019-07-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-08-01"), aes(x = TIMESTAMP, y = X570IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In570 2019-08-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-09-01"), aes(x = TIMESTAMP, y = X570IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In570 2019-09-01") + scale_color_d3()

#X650IN
ggplot(subset(gs, Date == "2019-06-01"), aes(x = TIMESTAMP, y = X650IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In650 2019-06-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-07-01"), aes(x = TIMESTAMP, y = X650IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In650 2019-07-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-08-01"), aes(x = TIMESTAMP, y = X650IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In650 2019-08-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-09-01"), aes(x = TIMESTAMP, y = X650IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In650 2019-09-01") + scale_color_d3()

#X810IN
ggplot(subset(gs, Date == "2019-06-01"), aes(x = TIMESTAMP, y = X810IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In810 2019-06-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-07-01"), aes(x = TIMESTAMP, y = X810IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In810 2019-07-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-08-01"), aes(x = TIMESTAMP, y = X810IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In810 2019-08-01") + scale_color_d3()
ggplot(subset(gs, Date == "2019-09-01"), aes(x = TIMESTAMP, y = X810IN, color = as.factor(ID))) + geom_point() + ggtitle("Incoming Radiation In810 2019-09-01") + scale_color_d3()


#Quantify the difference between them 
temp_agg <- aggregate(gs[,c("X532IN","X570IN","X650IN","X810IN")], list("TIMESTAMP" = gs$TIMESTAMP), FUN = function(x){sd(x, na.rm =  TRUE)})
IR_sd <- tidyr::gather(temp_agg, wavelength, sd, X532IN:X810IN, factor_key = TRUE)
IR_sd <- IR_sd %>% mutate(Date = lubridate::date(TIMESTAMP),
                          Time = hour(TIMESTAMP)+minute(TIMESTAMP)/60+second(TIMESTAMP)/3600)
head(temp_agg)
ggplot(IR_sd, aes(x = TIMESTAMP, y = sd, color = wavelength))+geom_point() + scale_color_d3()
ggplot(noon_selection(IR_sd, 8, 18), aes(x = TIMESTAMP, y = sd, color = wavelength)) + geom_point() +scale_color_d3() + ylab("Standard Deviation") + xlab("Date")
```

##Average the incoming radiation 
```{r}
#aggregate over time 
temp_agg <- aggregate(gs[,c("X532IN","X570IN","X650IN","X810IN")], list("TIMESTAMP" = gs$TIMESTAMP), FUN = function(x){mean(x, na.rm =  TRUE, trim = 0.2)}) #average of 5 
names(temp_agg) <- c("TIMESTAMP","X532IN_mean","X570IN_mean","X650IN_mean","X810IN_mean")
#add these 4 new columns 
gs <- merge(gs, temp_agg, by = "TIMESTAMP")
head(gs)

#calculate reflectance and PRI, NDVI again 
gs <- gs %>% mutate(R532m = X532OUT/X532IN_mean, 
                    R570m = X570OUT/X570IN_mean,
                    R650m = X650OUT/X650IN_mean,
                    R810m = X810OUT/X810IN_mean,
                    PRIm = (R532m-R570m)/(R532m+R570m),
                    NDVIm = (R810m-R650m)/(R810m+R650m))


```

##Visualize the diurnal cycle of PRI 
```{r}
#remove 5 CONTROL DDD
unique(gs$ID)
gssb <- subset(gs, ID != "5 CONTROL DDD  " & ID!= "10 CIMIS  ")
#PRIm from 7:00 to 20:00
ggplot(subset(gssb, Date == "2019-06-01" & Time > 7 & Time < 19), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-06-01") + scale_color_d3() + ylab("PRI") + xlab("Time")
ggplot(subset(gssb, Date == "2019-07-01" & Time > 7 & Time < 19), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-07-01") + scale_color_d3() + ylab("PRI") + xlab("Time")
ggplot(subset(gssb, Date == "2019-08-01" & Time > 7 & Time < 19), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-08-01") + scale_color_d3() + ylab("PRI") + xlab("Time")
ggplot(subset(gssb, Date == "2019-09-01" & Time > 7 & Time < 19), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-09-01") + scale_color_d3() + ylab("PRI") + xlab("Time")


#PRIm from 9:00 to 18:00, choose the date that have ground measurements
p1 = ggplot(subset(gssb, Date == "2019-05-31" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-05-31") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p2 = ggplot(subset(gssb, Date == "2019-06-12" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-06-12") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p3 = ggplot(subset(gssb, Date == "2019-06-26" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-06-26") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p4 = ggplot(subset(gssb, Date == "2019-07-18" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-07-18") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p5 = ggplot(subset(gssb, Date == "2019-07-26" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-07-26") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p6 = ggplot(subset(gssb, Date == "2019-08-02" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-08-02") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p7 = ggplot(subset(gssb, Date == "2019-08-09" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-08-09") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
p8 = ggplot(subset(gssb, Date == "2019-08-15" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-08-15") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1) + theme(legend.position = "none")
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow = 2, ncol =4) 
#To generate the legend
ggplot(subset(gssb, Date == "2019-08-15" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = PRIm, color = as.factor(ID))) + geom_point() + ggtitle("PRI 2019-08-15") + scale_color_d3() + ylab("PRI") + xlab("Time") + ylim(-0.125, 0.1)


```
##How about NDVI
```{r}
#NDVIm from 9:00 to 18:00, choose the date that have ground measurements
p1 = ggplot(subset(gssb, Date == "2019-05-31" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-05-31") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p2 = ggplot(subset(gssb, Date == "2019-06-12" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-06-12") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p3 = ggplot(subset(gssb, Date == "2019-06-26" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-06-26") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p4 = ggplot(subset(gssb, Date == "2019-07-18" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-07-18") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p5 = ggplot(subset(gssb, Date == "2019-07-26" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-07-26") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p6 = ggplot(subset(gssb, Date == "2019-08-02" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-08-02") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p7 = ggplot(subset(gssb, Date == "2019-08-09" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-08-09") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
p8 = ggplot(subset(gssb, Date == "2019-08-15" & Time > 9 & Time < 18), aes(x = TIMESTAMP, y = NDVIm, color = as.factor(ID))) + geom_point() + ggtitle("NDVI 2019-08-15") + scale_color_d3() + ylab("NDVI") + xlab("Time")  + theme(legend.position = "none")+ ylim(0.4, 1)
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow = 2, ncol =4) 

```

#Seasonal Change
##function to calculate daily average
```{r}
PRIm_dayave <- function(data, early, late, begin, end){
  #between certain dates
  PRIm_date <- date_selection(data, begin, end)
  #noon average
  PRIm_date_noon <- noon_selection(PRIm_date, early, late)
  #split
  PRIm_split <- split(PRIm_date_noon, PRIm_date_noon$Date)
  #lapply
  PRIm_ave <- lapply(lapply(PRIm_split, "[[", 38), function(x){mean(x, na.rm = TRUE, trim = 0.2)})
  PRIm_ave <- data.frame("Date" = ymd(names(PRIm_ave)), "PRIm" = unlist(PRIm_ave))
  #result
  row.names(PRIm_ave) <- NULL
  return(PRIm_ave)
}

NDVIm_dayave <- function(data, early, late, begin, end){
  #between certain dates
  NDVIm_date <- date_selection(data, begin, end)
  #noon average
  NDVIm_date_noon <- noon_selection(NDVIm_date, early, late)
  #split
  NDVIm_split <- split(NDVIm_date_noon, NDVIm_date_noon$Date)
  #lapply
  NDVIm_ave <- lapply(lapply(NDVIm_split, "[[", 39), function(x){mean(x, na.rm = TRUE, trim = 0.2)})
  NDVIm_ave <- data.frame("Date" = ymd(names(NDVIm_ave)), "NDVIm" = unlist(NDVIm_ave))
  #result
  row.names(NDVIm_ave) <- NULL
  return(NDVIm_ave)
}
```

##Calculate PRIm and PRIm daily average 
```{r}
temp_split <- split(gssb, gssb$ID)
#PRIm daily average
temp_ls <- lapply(temp_split, function(x){PRIm_dayave(x, 11, 15, "2019-05-07", "2019-09-05")})
for(i in 1:length(temp_ls)){
  temp_ls[[i]]$ID = names(temp_ls)[i]
}
PRIm_daily <- do.call(rbind, temp_ls)
row.names(PRIm_daily) <- NULL
ggplot(PRIm_daily, aes(x = Date, y = PRIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI")+ggtitle("PRI Seasonal Change")


#Seasonal Change of NDVI
temp_ls <- lapply(temp_split, function(x){NDVIm_dayave(x, 11, 15, "2019-05-07", "2019-09-05")})
for(i in 1:length(temp_ls)){
  temp_ls[[i]]$ID = names(temp_ls)[i]
}
NDVIm_daily <- do.call(rbind, temp_ls)
row.names(NDVIm_daily) <- NULL
ggplot(NDVIm_daily, aes(x = Date, y = NDVIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("NDVI")+ggtitle("NDVI Seasonal Change")

#merge daily NDVI and daily PRI
gs_daily <- merge(PRIm_daily, NDVIm_daily, by = c("Date","ID"))
#add block name
gs_daily$BLOCK <- sapply(strsplit(gs_daily$ID, split = " "),'[',1)

#Divide into different blocks
##PRI
p1 = ggplot(subset(gs_daily, BLOCK == 2), aes(x = Date, y = PRIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI")+ggtitle("PRI Seasonal Change Block 2") + ylim(-0.1, 0.04)
p2 = ggplot(subset(gs_daily, BLOCK == 4), aes(x = Date, y = PRIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI")+ggtitle("PRI Seasonal Change Block 4")+ ylim(-0.1, 0.04)
p3 = ggplot(subset(gs_daily, BLOCK == 5), aes(x = Date, y = PRIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI")+ggtitle("PRI Seasonal Change Block 5")+ ylim(-0.1, 0.04)
grid.arrange(p1,p2,p3,nrow=3)
##NDVI
p1 = ggplot(subset(gs_daily, BLOCK == 2), aes(x = Date, y = NDVIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("NDVI")+ggtitle("NDVI Seasonal Change Block 2")
p2 = ggplot(subset(gs_daily, BLOCK == 4), aes(x = Date, y = NDVIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("NDVI")+ggtitle("NDVI Seasonal Change Block 4")
p3 = ggplot(subset(gs_daily, BLOCK == 5), aes(x = Date, y = NDVIm, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("NDVI")+ggtitle("NDVI Seasonal Change Block 5")
grid.arrange(p1,p2,p3,nrow=3)
```
##Corrected PRI
###PRI/NDVI
```{r}
gs_daily <- gs_daily %>% mutate(PRI.NDVI = PRIm/NDVIm)

##Plot
p1 = ggplot(subset(gs_daily, BLOCK == 2), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVI Seasonal Change Block 2")
p2 = ggplot(subset(gs_daily, BLOCK == 4), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVI Seasonal Change Block 4")
p3 = ggplot(subset(gs_daily, BLOCK == 5), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVINDVI Seasonal Change Block 5")
grid.arrange(p1,p2,p3,nrow=3)

##Subset after June
p1 = ggplot(subset(gs_daily, BLOCK == 2 & Date >= "2019-05-31"), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVI Seasonal Change Block 2")
p2 = ggplot(subset(gs_daily, BLOCK == 4 & Date >= "2019-05-31"), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVI Seasonal Change Block 4")
p3 = ggplot(subset(gs_daily, BLOCK == 5 & Date >= "2019-05-31"), aes(x = Date, y = PRI.NDVI, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRI/NDVI")+ggtitle("PRI/NDVINDVI Seasonal Change Block 5")
grid.arrange(p1,p2,p3,nrow=3)

```
###PRIscale-NDVIscale
```{r}
#scale both PRI and NDVI to (0,1) range
gs_daily <- gs_daily %>% mutate(PRI_scale = PRIm-min(PRIm, na.rm = TRUE)/(max(PRIm, na.rm = TRUE) - min(PRIm, na.rm = TRUE)),
                                NDVI_scale = NDVIm-min(NDVIm, na.rm = TRUE)/(max(NDVIm, na.rm = TRUE) - min(NDVIm, na.rm = TRUE)),
                                PRI_NDVI_scale = PRI_scale - NDVI_scale)

p1 = ggplot(subset(gs_daily, BLOCK == 2 & Date >= "2019-05-31"), aes(x = Date, y = PRI_NDVI_scale, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRIsc-NDVIsc")+ggtitle("PRI-NDVI Seasonal Change Block 2")
p2 = ggplot(subset(gs_daily, BLOCK == 4 & Date >= "2019-05-31"), aes(x = Date, y = PRI_NDVI_scale, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRIsc-NDVIsc")+ggtitle("PRI-NDVI Seasonal Change Block 4")
p3 = ggplot(subset(gs_daily, BLOCK == 5 & Date >= "2019-05-31"), aes(x = Date, y = PRI_NDVI_scale, color = ID)) + geom_line(size = 1) + scale_color_d3()+ylab("PRIsc-NDVIsc")+ggtitle("PRI-NDVINDVI Seasonal Change Block 5")
grid.arrange(p1,p2,p3,nrow=3)


```
#Include physiology measurement
##SWP
```{r}
path_phys <- "C:/Users/zt92/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/Physiology"
SWP_stands <- read_excel(file.path(path_phys, "SWP_stands.xlsx"))

head(SWP_stands)
unique(SWP_stands$TREATMENT)
str(SWP_stands)

SWP_stands$Date <- as.Date(SWP_stands$Date)
SWP_stands$ID <- paste(SWP_stands$BLOCK, SWP_stands$TREATMENT, sep = " ")
unique(SWP_stands$ID)

#trim the space 
gs_daily$ID <- trimws(gs_daily$ID, which  = "right")

#merge 
gs_daily_swp <- merge(gs_daily, SWP_stands, by = c("ID","Date"))
dim(gs_daily_swp)
dim(gs_daily)
dim(SWP_stands)

#plot
ggplot(gs_daily_swp, aes(x = Date, y = SWP, color = ID)) + geom_point() + scale_color_d3()

ggplot(subset(gs_daily_swp, Date != "2019-05-31"), aes(y = -SWP, x = PRI_NDVI_scale)) + geom_point(aes(color = as.factor(Date))) + scale_color_d3() + geom_smooth(method = "lm") + ylab("Stem Water Potential (Bars)") + xlab("PRIsc-NDVIsc")

lm1 <- lm(-SWP~PRI_NDVI_scale, subset(gs_daily_swp, Date != "2019-05-31"))
summary(lm1)
cor(subset(gs_daily_swp, Date != "2019-05-31")$PRI_NDVI_scale, subset(gs_daily_swp, Date != "2019-05-31")$SWP)^2
```

#Include weather data
```{r}

```

#Include UAV data
##Shapefiles
```{r}
path_shp <- "C:/Users/zt92/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/tomato_GCPs"
sensors_shp <- shapefile(file.path(path_shp, "sensors_tomato_2019.shp"))

path_macaw <- "C:/Users/zt92/Box Sync/BIOSTIMULANT FIELD SCREENING MASTER FOLDER/DRONE/macaw_pri"
macaw_pri_062819 <- raster(file.path(path_macaw, 'pri_062819.tif'))
macaw_pri_080219 <- raster(file.path(path_macaw, 'pri_080219.tif'))
macaw_pri_081019 <- raster(file.path(path_macaw, 'pri_081019.tif'))
macaw_pri_081519 <- raster(file.path(path_macaw, 'pri_081519.tif'))
macaw_pri_082219 <- raster(file.path(path_macaw, 'pri_082219.tif'))

uav_pri_062819 <- extract()

```


