---
title: "tomato_macaw_2019"
author: "Zhehan"
date: "January 6, 2020"
output: html_document
---
#Packages
```{r}
library(raster)
library(ggplot2)
library(dplyr)
library(stringr)
library(EBImage)
library(readxl)
library(caret)
library(Metrics)
library(tidyr)
library(ggthemes)
library(ggpubr)
library(tidyr)
```

#Shapefiles
##From the server
```{r}
path_shp <- "/z0/zt92/Tomato_biomass/tomato_analysis_2019/shapefiles"
#path_shp <- "Z:/CC_UCD_atRR/data2/UAV_MeeraeTomato/shapefiles"

rows_2019 <- shapefile(file.path(path_shp, "tomato_rows_2019.shp"))



rows_2019_cen1ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen1ft"))
rows_2019_cen2ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen2ft"))
rows_2019_cen3ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen3ft"))

```
##From laptop
```{r}
path_shp <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/shapefiles"
#use the adjusted one
flagbuff_2019 <- shapefile(file.path(path_shp, "flags_tomato_2019_adj_buffer.shp"))
rows_2019 <- shapefile(file.path(path_shp, "tomato_rows_2019.shp"))
rows_2019_cen1ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen1ft"))
rows_2019_cen2ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen2ft"))
rows_2019_cen3ft <- shapefile(file.path(path_shp, "tomato_rows_2019_cen3ft"))

length(unique(flagbuff_2019$Row))
length(unique(flagbuff_2019$Plot))
unique(flagbuff_2019$Plot)
unique(flagbuff_2019$Row)
ls_flag <- split(flagbuff_2019, flagbuff_2019$Row)
ls_flag[[1]]
plot(ls_flag[[1]])
```

#Read Micasense imgs
##function 
```{r}
read_uav <- function(path, stacks){
  #read raster layer, and crop with the extent
  uav_stacks <- raster::brick(file.path(path, stacks))
  #rename the bands
  names(uav_stacks) <- c("blue","green","red","rededge","nir","ndvi")
  
  return(uav_stacks)
}
```
##read micasense 
```{r}
path_uav <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/UAV processed images"
uav_061219 <- read_uav(path_uav, "tomato_061219_stacks2.tif")
uav_062819 <- read_uav(path_uav, "tomato_062819_stacks2.tif")
uav_071219 <- read_uav(path_uav, "tomato_071219_stacks.dat")
uav_071719 <- read_uav(path_uav, "tomato_071719_stacks2.tif")
uav_072619 <- read_uav(path_uav, "tomato_072619_stacks2.tif")
uav_080219 <- read_uav(path_uav, "tomato_080219_stacks2.tif")
uav_081019 <- read_uav(path_uav, "tomato_081019_stacks2.tif")
uav_081519 <- read_uav(path_uav, "tomato_081519_stacks2.tif")
uav_082219 <- read_uav(path_uav, "tomato_082219_stacks2.tif")
```
##crop to boundary and calculate NDVI histogram
```{r}
path_shp <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/shapefiles"
BND <- shapefile(file.path(path_shp, "tomato_BND_2019.shp"))
plot(BND)
uav_061219 <- raster::crop(uav_061219, BND)
values(uav_061219)[values(uav_061219) == -10000] <- NA
uav_062819 <- raster::crop(uav_062819, BND)
values(uav_062819)[values(uav_062819) == -10000] <- NA
uav_071219 <- raster::crop(uav_071219, BND)
values(uav_071219)[values(uav_071219) == -10000] <- NA
uav_071719 <- raster::crop(uav_071719, BND)
values(uav_071719)[values(uav_071719) == -10000] <- NA
uav_072619 <- raster::crop(uav_072619, BND)
values(uav_072619)[values(uav_072619) == -10000] <- NA
uav_080219 <- raster::crop(uav_080219, BND)
values(uav_080219)[values(uav_080219) == -10000] <- NA
uav_081019 <- raster::crop(uav_081019, BND)
values(uav_081019)[values(uav_081019) == -10000] <- NA
uav_081519 <- raster::crop(uav_081519, BND)
values(uav_081519)[values(uav_081519) == -10000] <- NA
uav_082219 <- raster::crop(uav_082219, BND)
values(uav_082219)[values(uav_082219) == -10000] <- NA


#convert to array and apply Otsu method
##0612
temp_arr <- raster::as.array(uav_061219$ndvi)
thr_uavndvi_061219 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_061219  #0.5409
hist(temp_arr, main = "UAV NDVI 061219", xlab = "NDVI")
##0628
temp_arr <- raster::as.array(uav_062819$ndvi)
thr_uavndvi_062819 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_062819  #0.5890
hist(temp_arr, main = "UAV NDVI 062819", xlab = "NDVI")
##0712
temp_arr <- raster::as.array(uav_071219$ndvi)
thr_uavndvi_071219 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_071219  #0.5974
hist(temp_arr, main = "UAV NDVI 071219", xlab = "NDVI")
##0717
temp_arr <- raster::as.array(uav_071719$ndvi)
thr_uavndvi_071719 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_071719  #0.5978
hist(temp_arr, main = "UAV NDVI 071719", xlab = "NDVI")
##0726
temp_arr <- raster::as.array(uav_072619$ndvi)
thr_uavndvi_072619 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_072619  #0.5940
hist(temp_arr, main = "UAV NDVI 072619", xlab = "NDVI")
##0802
temp_arr <- raster::as.array(uav_080219$ndvi)
thr_uavndvi_080219 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_080219  #0.6093
hist(temp_arr, main = "UAV NDVI 080219", xlab = "NDVI")
##0810
temp_arr <- raster::as.array(uav_081019$ndvi)
thr_uavndvi_081019 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_081019  #0.5409
hist(temp_arr, main = "UAV NDVI 081019", xlab = "NDVI")
##0815
temp_arr <- raster::as.array(uav_081519$ndvi)
thr_uavndvi_081519 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_081519  #0.5409
hist(temp_arr, main = "UAV NDVI 081519", xlab = "NDVI")
##0822
temp_arr <- raster::as.array(uav_082219$ndvi)
thr_uavndvi_082219 <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 256)
thr_uavndvi_082219  #0.5409
hist(temp_arr, main = "UAV NDVI 082219", xlab = "NDVI")
```

##Vegetation Mask
###Use a threshold as 0.6
```{r}
#vegetation mask
veg_061219_ms_0.6 <- reclassify(uav_061219$ndvi, cbind(-Inf, 0.6, NA))
veg_061219_ms_0.5 <- reclassify(uav_061219$ndvi, cbind(-Inf, 0.5, NA))
veg_062819_ms_0.6 <- reclassify(uav_062819$ndvi, cbind(-Inf, 0.6, NA))
veg_062819_ms_0.5 <- reclassify(uav_062819$ndvi, cbind(-Inf, 0.5, NA))
veg_071219_ms_0.6 <- reclassify(uav_071219$ndvi, cbind(-Inf, 0.6, NA))
veg_071219_ms_0.5 <- reclassify(uav_071219$ndvi, cbind(-Inf, 0.5, NA))
veg_071719_ms_0.6 <- reclassify(uav_071719$ndvi, cbind(-Inf, 0.6, NA))
veg_071719_ms_0.5 <- reclassify(uav_071719$ndvi, cbind(-Inf, 0.5, NA))
veg_072619_ms_0.6 <- reclassify(uav_072619$ndvi, cbind(-Inf, 0.6, NA))
veg_072619_ms_0.5 <- reclassify(uav_072619$ndvi, cbind(-Inf, 0.5, NA))
veg_080219_ms_0.6 <- reclassify(uav_080219$ndvi, cbind(-Inf, 0.6, NA))
veg_080219_ms_0.5 <- reclassify(uav_080219$ndvi, cbind(-Inf, 0.5, NA))
veg_081019_ms_0.6 <- reclassify(uav_081019$ndvi, cbind(-Inf, 0.6, NA))
veg_081019_ms_0.5 <- reclassify(uav_081019$ndvi, cbind(-Inf, 0.5, NA))
veg_081519_ms_0.6 <- reclassify(uav_081519$ndvi, cbind(-Inf, 0.6, NA))
veg_081519_ms_0.5 <- reclassify(uav_081519$ndvi, cbind(-Inf, 0.5, NA))
veg_082219_ms_0.6 <- reclassify(uav_082219$ndvi, cbind(-Inf, 0.6, NA))
veg_082219_ms_0.5 <- reclassify(uav_082219$ndvi, cbind(-Inf, 0.5, NA))

#apply the mask
uav_061219_masked0.5 <- raster::mask(uav_061219, veg_061219_ms_0.5)
uav_061219_masked0.6 <- raster::mask(uav_061219, veg_061219_ms_0.6)
uav_062819_masked0.5 <- raster::mask(uav_062819, veg_062819_ms_0.5)
uav_062819_masked0.6 <- raster::mask(uav_062819, veg_062819_ms_0.6)
uav_071219_masked0.5 <- raster::mask(uav_071219, veg_071219_ms_0.5)
uav_071219_masked0.6 <- raster::mask(uav_071219, veg_071219_ms_0.6)
uav_071719_masked0.5 <- raster::mask(uav_071719, veg_071719_ms_0.5)
uav_071719_masked0.6 <- raster::mask(uav_071719, veg_071719_ms_0.6)
uav_072619_masked0.5 <- raster::mask(uav_072619, veg_072619_ms_0.5)
uav_072619_masked0.6 <- raster::mask(uav_072619, veg_072619_ms_0.6)
uav_080219_masked0.5 <- raster::mask(uav_080219, veg_080219_ms_0.5)
uav_080219_masked0.6 <- raster::mask(uav_080219, veg_080219_ms_0.6)
uav_081019_masked0.5 <- raster::mask(uav_081019, veg_081019_ms_0.5)
uav_081019_masked0.6 <- raster::mask(uav_081019, veg_081019_ms_0.6)
uav_081519_masked0.5 <- raster::mask(uav_081519, veg_081519_ms_0.5)
uav_081519_masked0.6 <- raster::mask(uav_081519, veg_081519_ms_0.6)
uav_082219_masked0.5 <- raster::mask(uav_082219, veg_082219_ms_0.5)
uav_082219_masked0.6 <- raster::mask(uav_082219, veg_082219_ms_0.6)

#write the result
path_output_ms <- "D:/Micasense_tomato/Outputs"
writeRaster(uav_061219_masked0.5, file.path(path_output_ms, "uav_061219_masked0.5.tif"))
writeRaster(uav_061219_masked0.6, file.path(path_output_ms, "uav_061219_masked0.6.tif"))
writeRaster(uav_062819_masked0.5, file.path(path_output_ms, "uav_062819_masked0.5.tif"))
writeRaster(uav_062819_masked0.6, file.path(path_output_ms, "uav_062819_masked0.6.tif"))
writeRaster(uav_071219_masked0.5, file.path(path_output_ms, "uav_071219_masked0.5.tif"))
writeRaster(uav_071219_masked0.6, file.path(path_output_ms, "uav_071219_masked0.6.tif"))
writeRaster(uav_071719_masked0.5, file.path(path_output_ms, "uav_071719_masked0.5.tif"))
writeRaster(uav_071719_masked0.6, file.path(path_output_ms, "uav_071719_masked0.6.tif"))
writeRaster(uav_072619_masked0.5, file.path(path_output_ms, "uav_072619_masked0.5.tif"))
writeRaster(uav_072619_masked0.6, file.path(path_output_ms, "uav_072619_masked0.6.tif"))
writeRaster(uav_080219_masked0.5, file.path(path_output_ms, "uav_080219_masked0.5.tif"))
writeRaster(uav_080219_masked0.6, file.path(path_output_ms, "uav_080219_masked0.6.tif"))
writeRaster(uav_081019_masked0.5, file.path(path_output_ms, "uav_081019_masked0.5.tif"))
writeRaster(uav_081019_masked0.6, file.path(path_output_ms, "uav_081019_masked0.6.tif"))
writeRaster(uav_081519_masked0.5, file.path(path_output_ms, "uav_081519_masked0.5.tif"))
writeRaster(uav_081519_masked0.6, file.path(path_output_ms, "uav_081519_masked0.6.tif"))
writeRaster(uav_082219_masked0.5, file.path(path_output_ms, "uav_082219_masked0.5.tif"))
writeRaster(uav_082219_masked0.6, file.path(path_output_ms, "uav_082219_masked0.6.tif"))

#write the veg mask
writeRaster(veg_061219_ms_0.5, file.path(path_output_ms, "veg_061219_ms_0.5.tif"))
writeRaster(veg_061219_ms_0.6, file.path(path_output_ms, "veg_061219_ms_0.6.tif"))
writeRaster(veg_062819_ms_0.5, file.path(path_output_ms, "veg_062819_ms_0.5.tif"))
writeRaster(veg_062819_ms_0.6, file.path(path_output_ms, "veg_062819_ms_0.6.tif"))
writeRaster(veg_071219_ms_0.5, file.path(path_output_ms, "veg_071219_ms_0.5.tif"))
writeRaster(veg_071219_ms_0.6, file.path(path_output_ms, "veg_071219_ms_0.6.tif"))
writeRaster(veg_071719_ms_0.5, file.path(path_output_ms, "veg_071719_ms_0.5.tif"))
writeRaster(veg_071719_ms_0.6, file.path(path_output_ms, "veg_071719_ms_0.6.tif"))
writeRaster(veg_072619_ms_0.5, file.path(path_output_ms, "veg_072619_ms_0.5.tif"))
writeRaster(veg_072619_ms_0.6, file.path(path_output_ms, "veg_072619_ms_0.6.tif"))
writeRaster(veg_080219_ms_0.5, file.path(path_output_ms, "veg_080219_ms_0.5.tif"))
writeRaster(veg_080219_ms_0.6, file.path(path_output_ms, "veg_080219_ms_0.6.tif"))
writeRaster(veg_081019_ms_0.5, file.path(path_output_ms, "veg_081019_ms_0.5.tif"))
writeRaster(veg_081019_ms_0.6, file.path(path_output_ms, "veg_081019_ms_0.6.tif"))
writeRaster(veg_081519_ms_0.5, file.path(path_output_ms, "veg_081519_ms_0.5.tif"))
writeRaster(veg_081519_ms_0.6, file.path(path_output_ms, "veg_081519_ms_0.6.tif"))
writeRaster(veg_082219_ms_0.5, file.path(path_output_ms, "veg_082219_ms_0.5.tif"))
writeRaster(veg_082219_ms_0.6, file.path(path_output_ms, "veg_082219_ms_0.6.tif"))
#read from the laptop 

#remove the ndvi layers
rm(veg_061219_ms_0.5);rm(veg_061219_ms_0.6);rm(veg_062819_ms_0.5);rm(veg_062819_ms_0.6);rm(veg_071219_ms_0.5);rm(veg_071219_ms_0.6);rm(veg_071719_ms_0.5);rm(veg_071719_ms_0.6);rm(veg_072619_ms_0.5);rm(veg_072619_ms_0.6);rm(veg_080219_ms_0.5);rm(veg_080219_ms_0.6);rm(veg_081019_ms_0.5);rm(veg_081019_ms_0.6);rm(veg_081519_ms_0.5);rm(veg_081519_ms_0.6);rm(veg_082219_ms_0.5);rm(veg_082219_ms_0.6)
```
##Fruit mask

```{r}
hist(veg_082219_ms_0.6)
hist(uav_082219_masked0.6$ndvi)
temp_arr <- raster::as.array(uav_082219_masked0.6$ndvi)
thr_test <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 65536)
thr_test #0.776





#calculate redness
fruit_082219_1 <- uav_082219_masked0.6$red/uav_082219_masked0.6$green
writeRaster(fruit_082219_1, file.path(path_output_ms, "fruit_082219_1.tif"))

#calculate ExR
ExR_082219 <- uav_082219_masked0.6$red*1.4 - uav_082219_masked0.6$green
ExG_082219 <- uav_082219_masked0.6$green*2 - uav_082219_masked0.6$red - uav_082219_masked0.6$blue
ExGExR_082219 <- ExG_082219 - ExR_082219
writeRaster(ExR_082219, file.path(path_output_ms, "ExR_082219.tif"),overwrite = TRUE)
writeRaster(ExG_082219, file.path(path_output_ms, "ExG_082219.tif"),overwrite = TRUE)
writeRaster(ExGExR_082219, file.path(path_output_ms, "ExGExR_082219.tif"),overwrite = TRUE)
hist(ExR_082219)
hist(ExGExR_082219)
fruit_thr_082219 <- EBImage::otsu(as.array(ExGExR_082219), range = c(min(as.array(ExGExR_082219), na.rm = TRUE), max(as.array(ExGExR_082219), na.rm = TRUE)),levels = 65536)  #0.0648

#build the fruit mask 
fruit_ms_082219 <- reclassify(ExGExR_082219, cbind(-Inf, 0, NA))
#fruit_ms_082219 <- reclassify(ExGExR_082219, cbind(-Inf, fruit_thr_082219, NA))
writeRaster(fruit_ms_082219, file.path(path_output_ms, "fruit_ms_082219.tif"))
uav_082219_masked0.6_maskedfruit2 <- raster::mask(uav_082219_masked0.6, fruit_ms_082219)
writeRaster(uav_082219_masked0.6_maskedfruit2, file.path(path_output_ms, "uav_082219_masked0.6_maskedfruit2.tif"))
```
##buffer
```{r}
fruit_ms_082219_buff <- gBuffer(fruit_ms_082219, width = -0.027567)

```

##Erosion
```{r}
#combine two masks into one
vegfruitmask_082219 <- raster::merge(veg_082219_ms_0.6, fruit_ms_082219)
writeRaster(vegfruitmask_082219, file.path(path_output_ms,"vegfruitmask_082219.tif"))
erosion_082219 <- EBImage::erode(as.array(uav_082219_masked0.6_maskedfruit$ndvi), kern = makeBrush(3))
class(erosion_082219)
plot(erosion_082219)
a <- as.raster(erosion_082219)
```

##Shadow mask
###Function to calculate HSV
```{r}
rgbtohsv <- function(r,g,b){
  v = 1/3*(r+g+b)
  s = 1-3/(r+g+b)*min(r,g,b)
  ndi = (s-v)/(s+v)
  return(ndi)
}

hsv_test1 <- rgbtohsv(r = subset(uav_082219_masked0.6, 3), g = subset(uav_082219_masked0.6, 2), b = subset(uav_082219_masked0.6, 1))
#output
plot(hsv_test1)
hist(hsv_test1)
shadow_thr <- EBImage::otsu(as.array(hsv_test1), range = c(min(as.array(hsv_test1),na.rm = TRUE), max(as.array(hsv_test1), na.rm = TRUE)), levels = 65536) #0.6514
writeRaster(hsv_test1, file.path(path_output_ms, "hsvNDI_082219.tif"))


#build the binary mask 
shadow_ms_082219 <- reclassify(hsv_test1, cbind(shadow_thr, Inf, NA))
writeRaster(shadow_ms_082219, file.path(path_output_ms, "shadow_ms_082219.tif"))
#apply the mask
#uav_061219_masked0.5 <- raster::mask(uav_061219, veg_061219_ms_0.5)
uav_082219_masked0.6_maskedfruit_maskedshad <- raster::mask(uav_082219_masked0.6_maskedfruit, shadow_ms_082219)
writeRaster(uav_082219_masked0.6_maskedfruit_maskedshad, file.path(path_output_ms, "uav_082219_masked0.6_maskedfruit_maskedshad.tif"))
```

```{r}

hsv_test1 <- rgb2hsv(r = subset(uav_082219_masked0.6, 3), g = subset(uav_082219_masked0.6, 2), b = subset(uav_082219_masked0.6, 1), maxColorValue = 1)
hsv_test1 <- overlay(subset(uav_082219_masked0.6, 1:3), fun=rgb2hsv)
hsv_test <- raster::overlay(as.matrix(subset(uav_082219_masked0.6, 1:3)), fun = function(x){rgb2hsv(x, maxColorValue = 1)})
```
##Erosion morphological  
```{r}
test_erosion <- EBImage::erode()
```

##Extraction of the flag average
###Function of extraction
```{r}
ref_extract <- function(uav,shp, FUN, buff){
  ext_uav <- raster::extract(uav, shp, fun = FUN, na.rm = TRUE, df = TRUE, buffer = buff)
  ext_uav$Treatment <- shp$Treatment
  ext_uav$Side <- shp$Side
  ext_uav$Block <- shp$Block
  ext_uav$Row <- shp$Row
  #ext_uav$Plot <- shp$Plot
  return(ext_uav)
}

#for flagmean extraction 
ref_extract_flag <- function(uav,shp, FUN, buff){
  ext_uav <- raster::extract(uav, shp, fun = FUN, na.rm = TRUE, df = TRUE, buffer = buff)
  ext_uav$Treatment <- shp$Treatment
  ext_uav$Side <- shp$Side
  ext_uav$Block <- shp$Block
  ext_uav$Row <- shp$Row
  ext_uav$id <- shp$id
  ext_uav$Plant <- shp$Plant
  #ext_uav$Plot <- shp$Plot
  return(ext_uav)
}
```
###Extract different versions of mask  
```{r}
#0.5 as threshold
flagmean_uav_061219_masked0.5 <- ref_extract_flag(uav_061219_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_062819_masked0.5 <- ref_extract_flag(uav_062819_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_071219_masked0.5 <- ref_extract_flag(uav_071219_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_071719_masked0.5 <- ref_extract_flag(uav_071719_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_072619_masked0.5 <- ref_extract_flag(uav_072619_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_080219_masked0.5 <- ref_extract_flag(uav_080219_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_081019_masked0.5 <- ref_extract_flag(uav_081019_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_081519_masked0.5 <- ref_extract_flag(uav_081519_masked0.5, flagbuff_2019, mean, 0)
flagmean_uav_082219_masked0.5 <- ref_extract_flag(uav_082219_masked0.5, flagbuff_2019, mean, 0)
#0.6 as threshold
flagmean_uav_061219_masked0.6 <- ref_extract_flag(uav_061219_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_062819_masked0.6 <- ref_extract_flag(uav_062819_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_071219_masked0.6 <- ref_extract_flag(uav_071219_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_071719_masked0.6 <- ref_extract_flag(uav_071719_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_072619_masked0.6 <- ref_extract_flag(uav_072619_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_080219_masked0.6 <- ref_extract_flag(uav_080219_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_081019_masked0.6 <- ref_extract_flag(uav_081019_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_081519_masked0.6 <- ref_extract_flag(uav_081519_masked0.6, flagbuff_2019, mean, 0)
flagmean_uav_082219_masked0.6 <- ref_extract_flag(uav_082219_masked0.6, flagbuff_2019, mean, 0)
#no mask 
flagmean_uav_061219_nomask <- ref_extract_flag(uav_061219, flagbuff_2019, mean, 0)
flagmean_uav_062819_nomask <- ref_extract_flag(uav_062819, flagbuff_2019, mean, 0)
flagmean_uav_071219_nomask <- ref_extract_flag(uav_071219, flagbuff_2019, mean, 0)
flagmean_uav_071719_nomask <- ref_extract_flag(uav_071719, flagbuff_2019, mean, 0)
flagmean_uav_072619_nomask <- ref_extract_flag(uav_072619, flagbuff_2019, mean, 0)
flagmean_uav_080219_nomask <- ref_extract_flag(uav_080219, flagbuff_2019, mean, 0)
flagmean_uav_081019_nomask <- ref_extract_flag(uav_081019, flagbuff_2019, mean, 0)
flagmean_uav_081519_nomask <- ref_extract_flag(uav_081519, flagbuff_2019, mean, 0)
flagmean_uav_082219_nomask <- ref_extract_flag(uav_082219, flagbuff_2019, mean, 0)

```
###Combine different dates together
```{r}
#0.5
#add date
flagmean_uav_061219_masked0.5$Date <- as.Date("2019-06-12")
flagmean_uav_062819_masked0.5$Date <- as.Date("2019-06-28")
flagmean_uav_071219_masked0.5$Date <- as.Date("2019-07-12")
flagmean_uav_071719_masked0.5$Date <- as.Date("2019-07-17")
flagmean_uav_072619_masked0.5$Date <- as.Date("2019-07-26")
flagmean_uav_080219_masked0.5$Date <- as.Date("2019-08-02")
flagmean_uav_081019_masked0.5$Date <- as.Date("2019-08-10")
flagmean_uav_081519_masked0.5$Date <- as.Date("2019-08-15")
flagmean_uav_082219_masked0.5$Date <- as.Date("2019-08-22")
#combine them together
flagmean_uav_masked0.5 <- rbind(flagmean_uav_061219_masked0.5, flagmean_uav_062819_masked0.5, flagmean_uav_071219_masked0.5, flagmean_uav_071719_masked0.5, flagmean_uav_072619_masked0.5, flagmean_uav_080219_masked0.5, flagmean_uav_081019_masked0.5, flagmean_uav_081519_masked0.5, flagmean_uav_082219_masked0.5)

#0.6
#add date
flagmean_uav_061219_masked0.6$Date <- as.Date("2019-06-12")
flagmean_uav_062819_masked0.6$Date <- as.Date("2019-06-28")
flagmean_uav_071219_masked0.6$Date <- as.Date("2019-07-12")
flagmean_uav_071719_masked0.6$Date <- as.Date("2019-07-17")
flagmean_uav_072619_masked0.6$Date <- as.Date("2019-07-26")
flagmean_uav_080219_masked0.6$Date <- as.Date("2019-08-02")
flagmean_uav_081019_masked0.6$Date <- as.Date("2019-08-10")
flagmean_uav_081519_masked0.6$Date <- as.Date("2019-08-15")
flagmean_uav_082219_masked0.6$Date <- as.Date("2019-08-22")
#combine them together
flagmean_uav_masked0.6 <- rbind(flagmean_uav_061219_masked0.6, flagmean_uav_062819_masked0.6, flagmean_uav_071219_masked0.6, flagmean_uav_071719_masked0.6, flagmean_uav_072619_masked0.6, flagmean_uav_080219_masked0.6, flagmean_uav_081019_masked0.6, flagmean_uav_081519_masked0.6, flagmean_uav_082219_masked0.6)

#add date
flagmean_uav_061219_nomask$Date <- as.Date("2019-06-12")
flagmean_uav_062819_nomask$Date <- as.Date("2019-06-28")
flagmean_uav_071219_nomask$Date <- as.Date("2019-07-12")
flagmean_uav_071719_nomask$Date <- as.Date("2019-07-17")
flagmean_uav_072619_nomask$Date <- as.Date("2019-07-26")
flagmean_uav_080219_nomask$Date <- as.Date("2019-08-02")
flagmean_uav_081019_nomask$Date <- as.Date("2019-08-10")
flagmean_uav_081519_nomask$Date <- as.Date("2019-08-15")
flagmean_uav_082219_nomask$Date <- as.Date("2019-08-22")
#combine them together
flagmean_uav_nomask <- rbind(flagmean_uav_061219_nomask, flagmean_uav_062819_nomask, flagmean_uav_071219_nomask, flagmean_uav_071719_nomask, flagmean_uav_072619_nomask, flagmean_uav_080219_nomask, flagmean_uav_081019_nomask, flagmean_uav_081519_nomask, flagmean_uav_082219_nomask)

```


#Read macaw imgs
##read 12band macaw function 
```{r}
path_12bands <- "D:/MACAW_tomato"


read_12band <- function(path, stacks){
  uav_stacks <- raster::brick(file.path(path, stacks))
  #subset to 1:12
  uav_stacks <- subset(uav_stacks, 1:12)
  #rename 
  names(uav_stacks) <- c("X800","X450","X480","X530","X550","X570","X670","X700","X720","X740","X900","X970")
  return(uav_stacks)
}
```

##(Useless currently)read macaw function  
```{r}
read_macaw <- function(path, stacks){
  #read raster layer, and crop with the extent
  uav_stacks <- raster::brick(file.path(path, stacks))
  #rename the bands
  names(uav_stacks) <- c("p800","p570","p530")
  
  return(uav_stacks)
}


```
##Read 12band macaw from mobile hard drive
```{r}
path_12band <- "D:/MACAW_tomato"
macaw_082219 <- read_12band(path_12band, "agisoft_20190822_12bands_withgcps.tif")
macaw_082219
macaw_081519 <- read_12band(path_12band, "agisoft_20190815_12bands_withgcps.tif")
macaw_081519
macaw_081019 <- read_12band(path_12band, "agisoft_20190810_12bands_withgcps.tif")
macaw_081019
macaw_080219 <- read_12band(path_12band, "agisoft_20190802_12bands_withgcps.tif")
macaw_080219
macaw_062819 <- read_12band(path_12band, "agisoft_20190628_12bands_withgcps.tif")
macaw_062819
macaw_053119 <- read_12band(path_12band, "agisoft_20190531_12bands_withgcps.tif")
macaw_053119

```

##(Not useful)Read from local computer
```{r}
path_pri <- "C:/Users/tangz/Box Sync/BIOSTIMULANT FIELD SCREENING MASTER FOLDER/DRONE/macaw_pri"

#0822
macaw_082219 <- read_macaw(path_pri, "tomato_macawrgbpri_082219.tif")
pri_082219 <- (macaw_082219$p530 - macaw_082219$p570)/((macaw_082219$p530 + macaw_082219$p570))
writeRaster(pri_082219, file.path(path_pri, "pri_082219.tif"))
#0815
macaw_081519 <- read_macaw(path_pri, "tomato_macawrgbpri_081519.tif")
pri_081519 <- (macaw_081519$p530 - macaw_081519$p570)/((macaw_081519$p530 + macaw_081519$p570))
writeRaster(pri_081519, file.path(path_pri, "pri_081519.tif"))
#0810
macaw_081019 <- read_macaw(path_pri, "tomato_macawrgbpri_081019.tif")
pri_081019 <- (macaw_081019$p530 - macaw_081019$p570)/((macaw_081019$p530 + macaw_081019$p570))
writeRaster(pri_081019, file.path(path_pri, "pri_081019.tif"))
#0802
macaw_080219 <- read_macaw(path_pri, "tomato_macawrgbpri_080219.tif")
pri_080219 <- (macaw_080219$p530 - macaw_080219$p570)/((macaw_080219$p530 + macaw_080219$p570))
writeRaster(pri_080219, file.path(path_pri, "pri_080219.tif"))
#0628
macaw_062819 <- read_macaw(path_pri, "tomato_macawrgbpri_062819.tif")
pri_062819 <- (macaw_062819$p530 - macaw_062819$p570)/((macaw_062819$p530 + macaw_062819$p570))
writeRaster(pri_062819, file.path(path_pri, "pri_062819.tif"))


```


##Read fom the server
```{r}
path_pri_server <- "/z0/zt92/Tomato_biomass/tomato_analysis_2019/outputs"
pri_062819 <- raster(file.path(path_pri_server, 'pri_062819.tif'))
pri_080219 <- raster(file.path(path_pri_server, 'pri_080219.tif'))
pri_081019 <- raster(file.path(path_pri_server, 'pri_081019.tif'))
pri_081519 <- raster(file.path(path_pri_server, 'pri_081519.tif'))
pri_082219 <- raster(file.path(path_pri_server, 'pri_082219.tif'))
```


#Vegetation mask
##Calculate NDVI
```{r}
ndvi_053119 <- (macaw_053119$X800-macaw_053119$X670)/(macaw_053119$X800+macaw_053119$X670)
ndvi_062819 <- (macaw_062819$X800-macaw_062819$X670)/(macaw_062819$X800+macaw_062819$X670)
ndvi_080219 <- (macaw_080219$X800-macaw_080219$X670)/(macaw_080219$X800+macaw_080219$X670)
#ndvi_081019 <- (macaw_081019$X800-macaw_081019$X670)/(macaw_081019$X800+macaw_081019$X670)
ndvi_081519 <- (macaw_081519$X800-macaw_081519$X670)/(macaw_081519$X800+macaw_081519$X670)
ndvi_082219 <- (macaw_082219$X800-macaw_082219$X670)/(macaw_082219$X800+macaw_082219$X670)

#add layer to the raster brick 
macaw_053119 <- addLayer(macaw_053119, ndvi_053119)
names(macaw_053119)[13] <- "NDVI"
macaw_062819 <- addLayer(macaw_062819, ndvi_062819)
names(macaw_062819)[13] <- "NDVI"
macaw_080219 <- addLayer(macaw_080219, ndvi_080219)
names(macaw_080219)[13] <- "NDVI"
#macaw_081019 <- addLayer(macaw_081019, ndvi_081019)
#names(macaw_081019)[13] <- "NDVI"
macaw_081519 <- addLayer(macaw_081519, ndvi_081519)
names(macaw_081519)[13] <- "NDVI"
macaw_082219 <- addLayer(macaw_082219, ndvi_082219)
names(macaw_082219)[13] <- "NDVI"

#Output
path_output <- "D:/MACAW_tomato/Outputs"
writeRaster(ndvi_082219, file.path(path_output, "NDVI_082219.tif"))
writeRaster(ndvi_081519, file.path(path_output, "NDVI_081519.tif"))
writeRaster(ndvi_081019, file.path(path_output, "NDVI_081019.tif"))
writeRaster(ndvi_080219, file.path(path_output, "NDVI_080219.tif"))
writeRaster(ndvi_062819, file.path(path_output, "NDVI_062819.tif"))
writeRaster(ndvi_053119, file.path(path_output, "NDVI_053119.tif"))


#read ndvi 
path_output <- "D:/MACAW_tomato/Outputs"
ndvi_053119 <- raster(file.path(path_output, "NDVI_053119.tif"))
ndvi_062819 <- raster(file.path(path_output, "NDVI_062819.tif"))
ndvi_080219 <- raster(file.path(path_output, "NDVI_080219.tif"))
ndvi_081019 <- raster(file.path(path_output, "NDVI_081019.tif"))
ndvi_081519 <- raster(file.path(path_output, "NDVI_081519.tif"))


```
###Crop to boundary
```{r}
BND <- shapefile(file.path(path_shp, "tomato_BND_2019.shp"))
plot(BND, add = TRUE)
macaw_053119 <- raster::crop(macaw_053119, BND)
macaw_062819 <- raster::crop(macaw_062819, BND)
macaw_080219 <- raster::crop(macaw_080219, BND)
macaw_081019 <- raster::crop(macaw_081019, BND)
macaw_081519 <- raster::crop(macaw_081519, BND)
macaw_082219 <- raster::crop(macaw_082219, BND)

ndvi_053119 <- raster::crop(ndvi_053119, BND)
ndvi_062819 <- raster::crop(ndvi_062819, BND)
ndvi_080219 <- raster::crop(ndvi_080219, BND)
#ndvi_081019 <- raster::crop(ndvi_081019, BND)
ndvi_081519 <- raster::crop(ndvi_081519, BND)

```

##Vegetation mask
###use a threshold as 0.5
```{r}
#vegetation mask
veg_053119 <- reclassify(macaw_053119$NDVI, cbind(-Inf, 0.5, NA))
veg_062819 <- reclassify(macaw_062819$NDVI, cbind(-Inf, 0.5, NA))
veg_080219 <- reclassify(macaw_080219$NDVI, cbind(-Inf, 0.5, NA))
#veg_081019 <- reclassify(macaw_081019$NDVI, cbind(-Inf, 0.5, NA))
veg_081519 <- reclassify(macaw_081519$NDVI, cbind(-Inf, 0.5, NA))
veg_082219 <- reclassify(macaw_082219$NDVI, cbind(-Inf, 0.5, NA))

#apply the mask
macaw_053119_masked <- raster::mask(macaw_053119, veg_053119)
macaw_062819_masked <- raster::mask(macaw_062819, veg_062819)
macaw_080219_masked <- raster::mask(macaw_080219, veg_080219)
#macaw_081019_masked <- raster::mask(macaw_081019, veg_081019)
macaw_081519_masked <- raster::mask(macaw_081519, veg_081519)
macaw_082219_masked <- raster::mask(macaw_082219, veg_082219)

#write the result
path_output <- "D:/MACAW_tomato/Outputs"
writeRaster(macaw_053119_masked, file.path(path_output, "macaw_053119_masked0.5.tif"), overwrite = TRUE)
writeRaster(macaw_062819_masked, file.path(path_output, "macaw_062819_masked0.5.tif"), overwrite = TRUE)
writeRaster(macaw_080219_masked, file.path(path_output, "macaw_080219_masked0.5.tif"), overwrite = TRUE)
#writeRaster(macaw_081019_masked, file.path(path_output, "macaw_081019_masked0.5.tif"))
writeRaster(macaw_081519_masked, file.path(path_output, "macaw_081519_masked0.5.tif"),overwrite=  TRUE)
writeRaster(macaw_082219_masked, file.path(path_output, "macaw_082219_masked0.5.tif"), overwrite = TRUE)

#read from the laptop 

#remove the ndvi layers
rm(veg_062819);rm(veg_080219);rm(veg_081019);rm(veg_081519);rm(veg_082219)
rm(ndvi_062819);rm(ndvi_080219);rm(ndvi_081019);rm(ndvi_081519);rm(ndvi_082219)

```
###Buffer over the vegetation mask 
```{r}
#nonveg_053119 <- reclassify(ndvi_053119, cbind(0.5, Inf, NA))
nonveg_053119 <- reclassify(ndvi_053119, rbind(c(0.5, Inf, 0),c(-Inf, 0.5, 1)))
nonveg_062819 <- reclassify(ndvi_062819, rbind(c(0.5, Inf, 0),c(-Inf, 0.5, 1)))
nonveg_080219 <- reclassify(ndvi_080219, rbind(c(0.5, Inf, 0),c(-Inf, 0.5, 1)))
nonveg_081519 <- reclassify(ndvi_081519, rbind(c(0.5, Inf, 0),c(-Inf, 0.5, 1)))
#output the nonveg mask 
writeRaster(nonveg_053119, file.path(path_output, "nonveg_053119.tif"))
writeRaster(nonveg_062819, file.path(path_output, "nonveg_062819.tif"))
writeRaster(nonveg_080219, file.path(path_output, "nonveg_080219.tif"))
writeRaster(nonveg_081519, file.path(path_output, "nonveg_081519.tif"))
#convert raster to shapefile
nonveg_053119_shp <- raster::rasterToPolygons(nonveg_053119, fun = function(x){x>0})
nonveg_062819_shp <- raster::rasterToPolygons(nonveg_062819, fun = function(x){x>0})
nonveg_080219_shp <- raster::rasterToPolygons(nonveg_080219, fun = function(x){x>0})
nonveg_081519_shp <- raster::rasterToPolygons(nonveg_081519, fun = function(x){x>0})
#output the shapefile
shapefile(nonveg_053119_shp, filename = file.path(path_output, "nonveg_053119_shp.shp"))
shapefile(nonveg_062819_shp, filename = file.path(path_output, "nonveg_062819_shp.shp"))
shapefile(nonveg_080219_shp, filename = file.path(path_output, "nonveg_080219_shp.shp"))
shapefile(nonveg_081519_shp, filename = file.path(path_output, "nonveg_081519_shp.shp"))
#buffer around the shapefile 
nonveg_053119_shp_buff <- raster::buffer(nonveg_053119_shp, width = res(nonveg_053119)[1]*3)
nonveg_062819_shp_buff <- raster::buffer(nonveg_062819_shp, width = res(nonveg_053119)[1]*3)
nonveg_080219_shp_buff <- raster::buffer(nonveg_080219_shp, width = res(nonveg_053119)[1]*3)
nonveg_081519_shp_buff <- raster::buffer(nonveg_081519_shp, width = res(nonveg_053119)[1]*3)
#output the shapefile 
shapefile(nonveg_053119_shp_buff, filename = file.path(path_output, "nonveg_053119_shp_buff.shp"))
shapefile(nonveg_062819_shp_buff, filename = file.path(path_output, "nonveg_062819_shp_buff.shp"))
shapefile(nonveg_080219_shp_buff, filename = file.path(path_output, "nonveg_080219_shp_buff.shp"))
shapefile(nonveg_081519_shp_buff, filename = file.path(path_output, "nonveg_081519_shp_buff.shp"))


#convert raster to shapefile
nonveg_053119_shp <- raster::rasterToPolygons(nonveg_053119_2, fun = function(x){x>0})
writeRaster(nonveg_053119, file.path(path_output, "nonveg_053119.tif"))
writeRaster(nonveg_053119_2, file.path(path_output, "nonveg_053119_2.tif"))


```


#Read the masked MACAW images
```{r}
path_output <- "D:/MACAW_tomato/Outputs"
macaw_053119_masked <- raster::brick(file.path(path_output, "macaw_053119_masked0.5.tif"))
names(macaw_053119_masked) <- c("X800","X450","X480","X530","X550","X570","X670","X700","X720","X740","X900","X970","NDVI")
macaw_062819_masked <- raster::brick(file.path(path_output, "macaw_062819_masked0.5.tif"))
names(macaw_062819_masked) <- c("X800","X450","X480","X530","X550","X570","X670","X700","X720","X740","X900","X970","NDVI")
macaw_080219_masked <- raster::brick(file.path(path_output, "macaw_080219_masked0.5.tif"))
names(macaw_080219_masked) <- c("X800","X450","X480","X530","X550","X570","X670","X700","X720","X740","X900","X970","NDVI")
macaw_081519_masked <- raster::brick(file.path(path_output, "macaw_081519_masked0.5.tif"))
names(macaw_081519_masked) <- c("X800","X450","X480","X530","X550","X570","X670","X700","X720","X740","X900","X970","NDVI")


```
#Apply a buffer around the veg mask 
```{r}

veg_062819 <- reclassify(macaw_062819$NDVI, cbind(-Inf, 0.5, NA))

```

##Fruit mask
###before the veg mask 
```{r}
#062819
#ExR = 1.4Red-Green
ExR_062819_macaw_masked <- macaw_062819_masked$X670*1.4 - macaw_062819_masked$X550
#ExG = 2Green - Red - Blue
ExG_062819_macaw_masked <- macaw_062819_masked$X550*2 - macaw_062819_masked$X670 - macaw_062819_masked$X450
ExGExR_062819_macaw_masked <- ExG_062819_macaw_masked - ExR_062819_macaw_masked
hist(ExGExR_062819_macaw_masked)
#output
writeRaster(ExGExR_062819_macaw_masked, file.path(path_output, "ExGExR_062819_macaw_masked.tif"))
#calculate the threshold 
temp_arr <- as.array(ExGExR_062819_macaw_masked)
temp_thr <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 65536)  #-27366,92
#build the fruit mask
veg_exgexr_062819_macaw_masked <- reclassify(ExGExR_062819_macaw_masked, cbind(-Inf,0,NA))
macaw_062819_exgexrmasked <- raster::mask(macaw_062819_masked, veg_exgexr_062819_macaw_masked)
writeRaster(macaw_062819_exgexrmasked, file.path(path_output, "macaw_062819_exgexrmasked.tif"),overwrite = TRUE)


#080219 
#ExR = 1.4Red-Green
ExR_080219_macaw_masked <- macaw_080219_masked$X670*1.4 - macaw_080219_masked$X550
#ExG = 2Green - Red - Blue
ExG_080219_macaw_masked <- macaw_080219_masked$X550*2 - macaw_080219_masked$X670 - macaw_080219_masked$X450
ExGExR_080219_macaw_masked <- ExG_080219_macaw_masked - ExR_080219_macaw_masked
hist(ExGExR_080219_macaw_masked)
#output
writeRaster(ExGExR_080219_macaw_masked, file.path(path_output, "ExGExR_080219_macaw_masked.tif"))
#calculate the threshold 
temp_arr <- as.array(ExGExR_080219_macaw_masked)
temp_thr <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 65536)  #-50047.14
temp_thr
#build the fruit mask
veg_exgexr_080219_macaw_masked <- reclassify(ExGExR_080219_macaw_masked, cbind(-Inf,0,NA))
macaw_080219_exgexrmasked <- raster::mask(macaw_080219_masked, veg_exgexr_080219_macaw_masked)
writeRaster(macaw_080219_exgexrmasked, file.path(path_output, "macaw_080219_exgexrmasked.tif"), overwrite = TRUE)

#0815
#081519
#ExR = 1.4Red-Green
ExR_081519_macaw_masked <- macaw_081519_masked$X670*1.4 - macaw_081519_masked$X550
#ExG = 2Green - Red - Blue
ExG_081519_macaw_masked <- macaw_081519_masked$X550*2 - macaw_081519_masked$X670 - macaw_081519_masked$X450
ExGExR_081519_macaw_masked <- ExG_081519_macaw_masked - ExR_081519_macaw_masked
hist(ExGExR_081519_macaw_masked)
#output
writeRaster(ExGExR_081519_macaw_masked, file.path(path_output, "ExGExR_081519_macaw_masked.tif"))
#calculate the threshold 
temp_arr <- as.array(ExGExR_081519_macaw_masked)
temp_thr <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 65536)  #-42245.6
temp_thr
#build the fruit mask
veg_exgexr_081519_macaw_masked <- reclassify(ExGExR_081519_macaw_masked, cbind(-Inf,0,NA))
macaw_081519_exgexrmasked <- raster::mask(macaw_081519_masked, veg_exgexr_081519_macaw_masked)
writeRaster(macaw_081519_exgexrmasked, file.path(path_output, "macaw_081519_exgexrmasked.tif"), overwrite = TRUE)

#0822
#ExR = 1.4Red-Green
ExR_082219_macaw_masked <- macaw_082219$X670*1.4 - macaw_082219$X550
#ExG = 2Green - Red - Blue
ExG_082219_macaw_masked <- macaw_082219$X550*2 - macaw_082219$X670 - macaw_082219$X450
ExGExR_082219_macaw_masked <- ExG_082219_macaw_masked - ExR_082219_macaw_masked
hist(ExGExR_082219_macaw_masked)
#output
writeRaster(ExGExR_082219_macaw_masked, file.path(path_output, "ExGExR_082219_macaw_masked.tif"))
#calculate the threshold 
temp_arr <- as.array(ExGExR_082219_macaw_masked)
temp_thr <- EBImage::otsu(temp_arr, range = c(min(temp_arr, na.rm = TRUE), max(temp_arr, na.rm = TRUE)), levels = 65536)  #-27366.92
#build the fruit mask
veg_exgexr_082219_macaw_masked <- reclassify(ExGExR_082219_macaw_masked, cbind(-Inf,0,NA))
macaw_082219_exgexrmasked <- raster::mask(macaw_082219_masked, veg_exgexr_082219_macaw_masked)
writeRaster(macaw_082219_exgexrmasked, file.path(path_output, "macaw_082219_exgexrmasked.tif"))

```

###after the veg mask 
```{r}
#calculate ExR 


ExR_082219 <- uav_082219_masked0.6$red*1.4 - uav_082219_masked0.6$green
ExG_082219 <- uav_082219_masked0.6$green*2 - uav_082219_masked0.6$red - uav_082219_masked0.6$blue
ExGExR_082219 <- ExG_082219 - ExR_082219
writeRaster(ExR_082219, file.path(path_output_ms, "ExR_082219.tif"),overwrite = TRUE)
writeRaster(ExG_082219, file.path(path_output_ms, "ExG_082219.tif"),overwrite = TRUE)
writeRaster(ExGExR_082219, file.path(path_output_ms, "ExGExR_082219.tif"),overwrite = TRUE)
hist(ExR_082219)
hist(ExGExR_082219)
fruit_thr_082219 <- EBImage::otsu(as.array(ExGExR_082219), range = c(min(as.array(ExGExR_082219), na.rm = TRUE), max(as.array(ExGExR_082219), na.rm = TRUE)),levels = 65536)  #0.0648

#build the fruit mask 
fruit_ms_082219 <- reclassify(ExGExR_082219, cbind(-Inf, 0, NA))
#fruit_ms_082219 <- reclassify(ExGExR_082219, cbind(-Inf, fruit_thr_082219, NA))
writeRaster(fruit_ms_082219, file.path(path_output_ms, "fruit_ms_082219.tif"))
uav_082219_masked0.6_maskedfruit2 <- raster::mask(uav_082219_masked0.6, fruit_ms_082219)
writeRaster(uav_082219_masked0.6_maskedfruit2, file.path(path_output_ms, "uav_082219_masked0.6_maskedfruit2.tif"))

```
###shadow mask 
```{r}
rgbtohsv <- function(r,g,b){
  r = r/65536
  g = g/65536
  b = b/65536
  v = 1/3*(r+g+b)
  s = 1-3/(r+g+b)*min(r,g,b)
  ndi = (s-v)/(s+v)
  return(ndi)
}

hsv_053119 <- rgbtohsv(r = subset(macaw_053119_masked,6), g = subset(macaw_053119_masked, 4), b = subset(macaw_053119_masked, 2))
writeRaster(hsv_053119, file.path(path_output, "hsv_053119.tif"))
hsv_062819 <- rgbtohsv(r = subset(macaw_062819_masked,6), g = subset(macaw_062819_masked, 4), b = subset(macaw_062819_masked, 2))
writeRaster(hsv_062819, file.path(path_output, "hsv_062819.tif"))
hsv_080219 <- rgbtohsv(r = subset(macaw_080219_masked,6), g = subset(macaw_080219_masked, 4), b = subset(macaw_080219_masked, 2))
writeRaster(hsv_080219, file.path(path_output, "hsv_080219.tif"))
hsv_081519 <- rgbtohsv(r = subset(macaw_081519_masked,6), g = subset(macaw_081519_masked, 4), b = subset(macaw_081519_masked, 2))
writeRaster(hsv_081519, file.path(path_output, "hsv_081519.tif"))

hist(hsv_053119)
hist(hsv_062819)
hsv_test1 <- rgbtohsv(r = subset(uav_082219_masked0.6, 3), g = subset(uav_082219_masked0.6, 2), b = subset(uav_082219_masked0.6, 1))
#output
plot(hsv_test1)
hist(hsv_test1)
shadow_thr <- EBImage::otsu(as.array(hsv_test1), range = c(min(as.array(hsv_test1),na.rm = TRUE), max(as.array(hsv_test1), na.rm = TRUE)), levels = 65536) #0.6514
writeRaster(hsv_test1, file.path(path_output_ms, "hsvNDI_082219.tif"))

```


###(Useless currently)Find threshold based on NDVI
```{r}
###convert to array 
ndvi_062819_arr <- raster::as.array(macaw_062819$NDVI)
thr_ndvi_062819 <- EBImage::otsu(ndvi_062819_arr, range = c(min(ndvi_062819_arr, na.rm = TRUE), max(ndvi_062819_arr, na.rm = TRUE)), levels = 256)
thr_ndvi_062819   #0.5313
hist(ndvi_062819_arr, main = "NDVI 2019-06-28", xlab = "NDVI")

ndvi_080219_arr <- raster::as.array(macaw_080219$NDVI)
thr_ndvi_080219 <- EBImage::otsu(ndvi_080219_arr, range = c(min(ndvi_080219_arr, na.rm = TRUE), max(ndvi_080219_arr, na.rm = TRUE)), levels = 256)
thr_ndvi_080219   #0.4882
hist(ndvi_080219_arr,main = "NDVI 2019-08-02", xlab = "NDVI")

ndvi_081019_arr <- raster::as.array(macaw_081019$NDVI)
thr_ndvi_081019 <- EBImage::otsu(ndvi_081019_arr, range = c(min(ndvi_081019_arr, na.rm = TRUE), max(ndvi_081019_arr, na.rm = TRUE)), levels = 256)
thr_ndvi_081019   #0.5586
hist(ndvi_081019_arr, main = "NDVI 2019-08-10", xlab = "NDVI")

ndvi_081519_arr <- raster::as.array(macaw_081519$NDVI)
thr_ndvi_081519 <- EBImage::otsu(ndvi_081519_arr, range = c(min(ndvi_081519_arr, na.rm = TRUE), max(ndvi_081519_arr, na.rm = TRUE)), levels = 256)
thr_ndvi_081519  #0.5745
hist(ndvi_081519_arr, main = "NDVI 2019-08-15", xlab = "NDVI")

ndvi_082219_arr <- raster::as.array(macaw_082219$NDVI)
thr_ndvi_082219 <- EBImage::otsu(ndvi_082219_arr, range = c(min(ndvi_082219_arr, na.rm = TRUE), max(ndvi_082219_arr, na.rm = TRUE)), levels = 256)
thr_ndvi_082219  #0.06599
hist(ndvi_082219_arr)


```

```{r}

```

##(Useless)Read vegetation mask
```{r}
path_pri_server <- "/z0/zt92/Tomato_biomass/tomato_analysis_2019/outputs"
veg_062819 <- raster(file.path(path_pri_server,"veg_062819_ndvi0.7.tif"))
veg_080219 <- raster(file.path(path_pri_server,"veg_080219_ndvi0.7.tif"))
veg_081019 <- raster(file.path(path_pri_server,"veg_081019_ndvi0.7.tif"))
veg_081519 <- raster(file.path(path_pri_server,"veg_081519_ndvi0.7.tif"))
veg_082219 <- raster(file.path(path_pri_server,"veg_082219_ndvi0.7.tif"))

```
##(Useless)Apply mask
```{r}
pri_062819_masked <- raster::mask(pri_062819, resample(veg_062819, pri_062819))
pri_080219_masked <- raster::mask(pri_080219, resample(veg_080219, pri_080219))
pri_081019_masked <- raster::mask(pri_081019, resample(veg_081019, pri_081019))
pri_081519_masked <- raster::mask(pri_081519, resample(veg_081519, pri_081519))
pri_082219_masked <- raster::mask(pri_082219, resample(veg_082219, pri_082219))

```



#Extraction 
##Function
```{r}
#for rowmean extraction
ref_extract <- function(uav,shp, FUN, buff){
  ext_uav <- raster::extract(uav, shp, fun = FUN, na.rm = TRUE, df = TRUE, buffer = buff)
  ext_uav$Treatment <- shp$Treatment
  ext_uav$Side <- shp$Side
  ext_uav$Block <- shp$Block
  ext_uav$Row <- shp$Row
  #ext_uav$Plot <- shp$Plot
  return(ext_uav)
}

#for flagmean extraction 
ref_extract_flag <- function(uav,shp, FUN, buff){
  ext_uav <- raster::extract(uav, shp, fun = FUN, na.rm = TRUE, df = TRUE, buffer = buff)
  ext_uav$Treatment <- shp$Treatment
  ext_uav$Side <- shp$Side
  ext_uav$Block <- shp$Block
  ext_uav$Row <- shp$Row
  ext_uav$id <- shp$id
  
  #ext_uav$Plot <- shp$Plot
  return(ext_uav)
}

```
##Extract from the plants around the flags
###with vegetation mask
```{r}
flagmean_macaw_053119 <- ref_extract_flag(macaw_053119_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_062819 <- ref_extract_flag(macaw_062819_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_080219 <- ref_extract_flag(macaw_080219_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
#flagmean_macaw_081019 <- ref_extract_flag(macaw_081019_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_081519 <- ref_extract_flag(macaw_081519_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_082219 <- ref_extract_flag(macaw_082219_masked, shp = flagbuff_2019, FUN = mean, buff = 0)

#add date
flagmean_macaw_053119$Date <- "2019-05-31"
flagmean_macaw_062819$Date <- "2019-06-28"
flagmean_macaw_080219$Date <- "2019-08-02"
flagmean_macaw_081519$Date <- "2019-08-15"
flagmean_macaw_082219$Date <- "2019-08-22"

#combine them 
flagmean_macaw <- rbind(flagmean_macaw_053119, flagmean_macaw_062819, flagmean_macaw_080219, flagmean_macaw_081519, flagmean_macaw_082219)

```
###with fruit mask
```{r}
#flagmean_macaw_frmask_053119 <- ref_extract_flag(macaw_053119_exgexrmasked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_exgexrmask_062819 <- ref_extract_flag(macaw_062819_exgexrmasked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_exgexrmask_080219 <- ref_extract_flag(macaw_080219_exgexrmasked, shp = flagbuff_2019, FUN = mean, buff = 0)
#flagmean_macaw_081019 <- ref_extract_flag(macaw_081019_masked, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_exgexrmask_081519 <- ref_extract_flag(macaw_081519_exgexrmasked, shp = flagbuff_2019, FUN = mean, buff = 0)
#$flagmean_macaw_exgexrmask_082219 <- ref_extract_flag(macaw_082219_exgexrmasked, shp = flagbuff_2019, FUN = mean, buff = 0)

#add date
#flagmean_macaw_exgexrmask_053119$Date <- "2019-05-31"
flagmean_macaw_exgexrmask_062819$Date <- "2019-06-28"
flagmean_macaw_exgexrmask_080219$Date <- "2019-08-02"
flagmean_macaw_exgexrmask_081519$Date <- "2019-08-15"
#flagmean_macaw_exgexrmask_082219$Date <- "2019-08-22"

#combine them 
flagmean_macaw_exgexrmask <- rbind(flagmean_macaw_exgexrmask_062819, flagmean_macaw_exgexrmask_080219, flagmean_macaw_exgexrmask_081519)
```


###without mask
```{r}
flagmean_macaw_062819_nomask <- ref_extract_flag(macaw_062819, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_080219_nomask <- ref_extract_flag(macaw_080219, shp = flagbuff_2019, FUN = mean, buff = 0)
#flagmean_macaw_081019_nomask <- ref_extract_flag(macaw_081019, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_081519_nomask <- ref_extract_flag(macaw_081519, shp = flagbuff_2019, FUN = mean, buff = 0)
flagmean_macaw_082219_nomask <- ref_extract_flag(macaw_082219, shp = flagbuff_2019, FUN = mean, buff = 0)

#add date
flagmean_macaw_062819_nomask$Date <- "2019-06-28"
flagmean_macaw_080219_nomask$Date <- "2019-08-02"
flagmean_macaw_081519_nomask$Date <- "2019-08-15"
flagmean_macaw_082219_nomask$Date <- "2019-08-22"

#combine them 
flagmean_macaw_nomask <- rbind(flagmean_macaw_062819_nomask, flagmean_macaw_080219_nomask, flagmean_macaw_081519_nomask, flagmean_macaw_082219_nomask)
```

##Extract from the rows
###053119 only
```{r}
path_df <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes"

#without mask 
rowmean_macaw_053119_nomask <- ref_extract(macaw_053119, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_053119_1ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_053119_2ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_053119_3ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_053119_nomask$Date <- "2019-05-31"
rowmean_macaw_053119_1ft_nomask$Date <- "2019-05-31"
rowmean_macaw_053119_2ft_nomask$Date <- "2019-05-31"
rowmean_macaw_053119_3ft_nomask$Date <- "2019-05-31"

#with mask
rowmean_macaw_053119 <- ref_extract(macaw_053119_masked, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_053119_1ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_053119_2ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_053119_3ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_053119$Date <- "2019-05-31"
rowmean_macaw_053119_1ft$Date <- "2019-05-31"
rowmean_macaw_053119_2ft$Date <- "2019-05-31"
rowmean_macaw_053119_3ft$Date <- "2019-05-31"

#output
##without mask 
write.csv(rowmean_macaw_053119_nomask, file.path(path_df, "rowmean_macaw_053119_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_1ft_nomask, file.path(path_df, "rowmean_macaw_053119_1ft_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_2ft_nomask, file.path(path_df, "rowmean_macaw_053119_2ft_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_3ft_nomask, file.path(path_df, "rowmean_macaw_053119_3ft_nomask.csv"), row.names = FALSE)
##with mask 
write.csv(rowmean_macaw_053119, file.path(path_df, "rowmean_macaw_053119.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_1ft, file.path(path_df, "rowmean_macaw_053119_1ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_2ft, file.path(path_df, "rowmean_macaw_053119_2ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_053119_3ft, file.path(path_df, "rowmean_macaw_053119_3ft.csv"), row.names = FALSE)


```

###Without masks
```{r}
#rowmean 
rowmean_macaw_053119_nomask <- ref_extract(macaw_053119, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_062819_nomask <- ref_extract(macaw_062819, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_080219_nomask <- ref_extract(macaw_080219, shp = rows_2019， FUN = mean, buff = 0)
#rowmean_macaw_081019_nomask <- ref_extract(macaw_081019, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_081519_nomask <- ref_extract(macaw_081519, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_082219_nomask <- ref_extract(macaw_082219, shp = rows_2019， FUN = mean, buff = 0)

#rowmean 1ft
rowmean_macaw_053119_1ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_062819_1ft_nomask <- ref_extract(macaw_062819, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_080219_1ft_nomask <- ref_extract(macaw_080219, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_1ft_nomask <- ref_extract(macaw_081019, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_081519_1ft_nomask <- ref_extract(macaw_081519, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_082219_1ft_nomask <- ref_extract(macaw_082219, shp = rows_2019_cen1ft， FUN = mean, buff = 0)

#rowmean 2ft
rowmean_macaw_053119_2ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_062819_2ft_nomask <- ref_extract(macaw_062819, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_080219_2ft_nomask <- ref_extract(macaw_080219, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_2ft_nomask <- ref_extract(macaw_081019, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_081519_2ft_nomask <- ref_extract(macaw_081519, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_082219_2ft_nomask <- ref_extract(macaw_082219, shp = rows_2019_cen2ft， FUN = mean, buff = 0)

#rowmean 3ft
rowmean_macaw_053119_3ft_nomask <- ref_extract(macaw_053119, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_062819_3ft_nomask <- ref_extract(macaw_062819, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_080219_3ft_nomask <- ref_extract(macaw_080219, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_3ft_nomask <- ref_extract(macaw_081019, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_081519_3ft_nomask <- ref_extract(macaw_081519, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_082219_3ft_nomask <- ref_extract(macaw_082219, shp = rows_2019_cen3ft， FUN = mean, buff = 0)


#add date
rowmean_macaw_062819_nomask$Date <- "2019-06-28"
rowmean_macaw_080219_nomask$Date <- "2019-08-02"
rowmean_macaw_081519_nomask$Date <- "2019-08-15"
rowmean_macaw_082219_nomask$Date <- "2019-08-22"
rowmean_macaw_062819_1ft_nomask$Date <- "2019-06-28"
rowmean_macaw_080219_1ft_nomask$Date <- "2019-08-02"
rowmean_macaw_081519_1ft_nomask$Date <- "2019-08-15"
rowmean_macaw_082219_1ft_nomask$Date <- "2019-08-22"
rowmean_macaw_062819_2ft_nomask$Date <- "2019-06-28"
rowmean_macaw_080219_2ft_nomask$Date <- "2019-08-02"
rowmean_macaw_081519_2ft_nomask$Date <- "2019-08-15"
rowmean_macaw_082219_2ft_nomask$Date <- "2019-08-22"
rowmean_macaw_062819_3ft_nomask$Date <- "2019-06-28"
rowmean_macaw_080219_3ft_nomask$Date <- "2019-08-02"
rowmean_macaw_081519_3ft_nomask$Date <- "2019-08-15"
rowmean_macaw_082219_3ft_nomask$Date <- "2019-08-22"

#combine them together
rowmean_macaw_nomask <- rbind(rowmean_macaw_062819_nomask, rowmean_macaw_080219_nomask, rowmean_macaw_081519_nomask, rowmean_macaw_082219_nomask)
rowmean_macaw_1ft_nomask <- rbind(rowmean_macaw_062819_1ft_nomask, rowmean_macaw_080219_1ft_nomask, rowmean_macaw_081519_1ft_nomask, rowmean_macaw_082219_1ft_nomask)
rowmean_macaw_2ft_nomask <- rbind(rowmean_macaw_062819_2ft_nomask, rowmean_macaw_080219_2ft_nomask, rowmean_macaw_081519_2ft_nomask, rowmean_macaw_082219_2ft_nomask)
rowmean_macaw_3ft_nomask <- rbind(rowmean_macaw_062819_3ft_nomask, rowmean_macaw_080219_3ft_nomask, rowmean_macaw_081519_3ft_nomask, rowmean_macaw_082219_3ft_nomask)

#output
write.csv(rowmean_macaw_nomask, file.path(path_df, "rowmean_macaw_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_1ft_nomask, file.path(path_df, "rowmean_macaw_1ft_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_2ft_nomask, file.path(path_df, "rowmean_macaw_2ft_nomask.csv"), row.names = FALSE)
write.csv(rowmean_macaw_3ft_nomask, file.path(path_df, "rowmean_macaw_3ft_nomask.csv"), row.names = FALSE)

```
###With masks
```{r}
rowmean_macaw_053119 <- ref_extract(macaw_053119_masked, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_053119_1ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_053119_2ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_053119_3ft <- ref_extract(macaw_053119_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_053119$Date <- "2019-06-28"
rowmean_macaw_053119_1ft$Date <- "2019-06-28"
rowmean_macaw_053119_2ft$Date <- "2019-06-28"
rowmean_macaw_053119_3ft$Date <- "2019-06-28"



#rowmean 
rowmean_macaw_062819 <- ref_extract(macaw_062819_masked, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_080219 <- ref_extract(macaw_080219_masked, shp = rows_2019， FUN = mean, buff = 0)
#rowmean_macaw_081019 <- ref_extract(macaw_081019_masked, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_081519 <- ref_extract(macaw_081519_masked, shp = rows_2019， FUN = mean, buff = 0)
rowmean_macaw_082219 <- ref_extract(macaw_082219_masked, shp = rows_2019， FUN = mean, buff = 0)

#rowmean 1ft
rowmean_macaw_062819_1ft <- ref_extract(macaw_062819_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_080219_1ft <- ref_extract(macaw_080219_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_1ft <- ref_extract(macaw_081019_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_081519_1ft <- ref_extract(macaw_081519_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)
rowmean_macaw_082219_1ft <- ref_extract(macaw_082219_masked, shp = rows_2019_cen1ft， FUN = mean, buff = 0)

#rowmean 2ft
rowmean_macaw_062819_2ft <- ref_extract(macaw_062819_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_080219_2ft <- ref_extract(macaw_080219_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_2ft <- ref_extract(macaw_081019_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_081519_2ft <- ref_extract(macaw_081519_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)
rowmean_macaw_082219_2ft <- ref_extract(macaw_082219_masked, shp = rows_2019_cen2ft， FUN = mean, buff = 0)

#rowmean 3ft
rowmean_macaw_062819_3ft <- ref_extract(macaw_062819_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_080219_3ft <- ref_extract(macaw_080219_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
#rowmean_macaw_081019_3ft <- ref_extract(macaw_081019_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_081519_3ft <- ref_extract(macaw_081519_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)
rowmean_macaw_082219_3ft <- ref_extract(macaw_082219_masked, shp = rows_2019_cen3ft， FUN = mean, buff = 0)


#add date
rowmean_macaw_062819$Date <- "2019-06-28"
rowmean_macaw_080219$Date <- "2019-08-02"
rowmean_macaw_081519$Date <- "2019-08-15"
rowmean_macaw_082219$Date <- "2019-08-22"
rowmean_macaw_062819_1ft$Date <- "2019-06-28"
rowmean_macaw_080219_1ft$Date <- "2019-08-02"
rowmean_macaw_081519_1ft$Date <- "2019-08-15"
rowmean_macaw_082219_1ft$Date <- "2019-08-22"
rowmean_macaw_062819_2ft$Date <- "2019-06-28"
rowmean_macaw_080219_2ft$Date <- "2019-08-02"
rowmean_macaw_081519_2ft$Date <- "2019-08-15"
rowmean_macaw_082219_2ft$Date <- "2019-08-22"
rowmean_macaw_062819_3ft$Date <- "2019-06-28"
rowmean_macaw_080219_3ft$Date <- "2019-08-02"
rowmean_macaw_081519_3ft$Date <- "2019-08-15"
rowmean_macaw_082219_3ft$Date <- "2019-08-22"

#combine them together
rowmean_macaw <- rbind(rowmean_macaw_062819, rowmean_macaw_080219, rowmean_macaw_081519, rowmean_macaw_082219)
rowmean_macaw_1ft <- rbind(rowmean_macaw_062819_1ft, rowmean_macaw_080219_1ft, rowmean_macaw_081519_1ft, rowmean_macaw_082219_1ft)
rowmean_macaw_2ft <- rbind(rowmean_macaw_062819_2ft, rowmean_macaw_080219_2ft, rowmean_macaw_081519_2ft, rowmean_macaw_082219_2ft)
rowmean_macaw_3ft <- rbind(rowmean_macaw_062819_3ft, rowmean_macaw_080219_3ft, rowmean_macaw_081519_3ft, rowmean_macaw_082219_3ft)

```


##(Useless currently)Extract row average after mask
```{r}
rowmean_pri_082219_2ft <- ref_extract(pri_082219_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_082219_3ft <- ref_extract(pri_082219_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_081519_2ft <- ref_extract(pri_081519_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_081519_3ft <- ref_extract(pri_081519_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_081019_2ft <- ref_extract(pri_081019_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_081019_3ft <- ref_extract(pri_081019_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_080219_2ft <- ref_extract(pri_080219_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_080219_3ft <- ref_extract(pri_080219_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_062819_2ft <- ref_extract(pri_062819_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_062819_3ft <- ref_extract(pri_062819_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_062819_2ft$Date <- as.Date("2019-06-28")
rowmean_pri_062819_3ft$Date <- as.Date("2019-06-28")
rowmean_pri_080219_2ft$Date <- as.Date("2019-08-02")
rowmean_pri_080219_3ft$Date <- as.Date("2019-08-02")
rowmean_pri_081019_2ft$Date <- as.Date("2019-08-10")
rowmean_pri_081019_3ft$Date <- as.Date("2019-08-10")
rowmean_pri_081519_2ft$Date <- as.Date("2019-08-15")
rowmean_pri_081519_3ft$Date <- as.Date("2019-08-15")
rowmean_pri_082219_2ft$Date <- as.Date("2019-08-22")
rowmean_pri_082219_3ft$Date <- as.Date("2019-08-22")
rowmean_pri <- rbind(rowmean_pri_062819, rowmean_pri_080219, rowmean_pri_081019, rowmean_pri_081519, rowmean_pri_082219)
rowmean_pri_1ft <- rbind(rowmean_pri_062819_1ft, rowmean_pri_080219_1ft, rowmean_pri_081019_1ft, rowmean_pri_081519_1ft, rowmean_pri_082219_1ft)
rowmean_pri_2ft <- rbind(rowmean_pri_062819_2ft, rowmean_pri_080219_2ft, rowmean_pri_081019_2ft, rowmean_pri_081519_2ft, rowmean_pri_082219_2ft)
rowmean_pri_3ft <- rbind(rowmean_pri_062819_3ft, rowmean_pri_080219_3ft, rowmean_pri_081019_3ft, rowmean_pri_081519_3ft, rowmean_pri_082219_3ft)
path_df_server <- "/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes"
#path_df <- "C:/Users/zt92/Box Sync/BIOSTIMULANT FIELD SCREENING MASTER FOLDER/DRONE/macaw_pri/dataframes"
write.csv(rowmean_pri, file.path(path_df_server, "rowmean_pri.csv"), row.names = FALSE)
write.csv(rowmean_pri_1ft, file.path(path_df_server, "rowmean_pri_1ft.csv"), row.names = FALSE)
write.csv(rowmean_pri_2ft, file.path(path_df_server, "rowmean_pri_2ft.csv"), row.names = FALSE)
write.csv(rowmean_pri_3ft, file.path(path_df_server, "rowmean_pri_3ft.csv"), row.names = FALSE)


#0822
rowmean_pri_082219 <- ref_extract(pri_082219_masked, shp = rows_2019, FUN = mean, buff = 0)
rowmean_pri_082219_1ft <- ref_extract(pri_082219_masked, shp = rows_2019_cen1ft, FUN = mean, buff = 0)
rowmean_pri_082219_2ft <- ref_extract(pri_082219_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_082219_3ft <- ref_extract(pri_082219_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_082219$Date <- as.Date("2019-08-22")
rowmean_pri_082219_1ft$Date <- as.Date("2019-08-22")
rowmean_pri_082219_2ft$Date <- as.Date("2019-08-22")
rowmean_pri_082219_3ft$Date <- as.Date("2019-08-22")


#0815
rowmean_pri_081519 <- ref_extract(pri_081519_masked, shp = rows_2019, FUN = mean, buff = 0)
rowmean_pri_081519_1ft <- ref_extract(pri_081519_masked, shp = rows_2019_cen1ft, FUN = mean, buff = 0)
rowmean_pri_081519_2ft <- ref_extract(pri_081519_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_081519_3ft <- ref_extract(pri_081519_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_081519$Date <- as.Date("2019-08-15")
rowmean_pri_081519_1ft$Date <- as.Date("2019-08-15")
rowmean_pri_081519_2ft$Date <- as.Date("2019-08-15")
rowmean_pri_081519_3ft$Date <- as.Date("2019-08-15")
save.image("/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes/envir1.RData")


#0810
rowmean_pri_081019 <- ref_extract(pri_081019_masked, shp = rows_2019, FUN = mean, buff = 0)
rowmean_pri_081019_1ft <- ref_extract(pri_081019_masked, shp = rows_2019_cen1ft, FUN = mean, buff = 0)
rowmean_pri_081019_2ft <- ref_extract(pri_081019_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_081019_3ft <- ref_extract(pri_081019_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_081019$Date <- as.Date("2019-08-10")
rowmean_pri_081019_1ft$Date <- as.Date("2019-08-10")
rowmean_pri_081019_2ft$Date <- as.Date("2019-08-10")
rowmean_pri_081019_3ft$Date <- as.Date("2019-08-10")
save.image("/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes/envir2.RData")


#0802
rowmean_pri_080219 <- ref_extract(pri_080219_masked, shp = rows_2019, FUN = mean, buff = 0)
rowmean_pri_080219_1ft <- ref_extract(pri_080219_masked, shp = rows_2019_cen1ft, FUN = mean, buff = 0)
rowmean_pri_080219_2ft <- ref_extract(pri_080219_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_080219_3ft <- ref_extract(pri_080219_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_080219$Date <- as.Date("2019-08-02")
rowmean_pri_080219_1ft$Date <- as.Date("2019-08-02")
rowmean_pri_080219_2ft$Date <- as.Date("2019-08-02")
rowmean_pri_080219_3ft$Date <- as.Date("2019-08-02")
save.image("/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes/envir3.RData")



#0628
rowmean_pri_062819 <- ref_extract(pri_062819_masked, shp = rows_2019, FUN = mean, buff = 0)
rowmean_pri_062819_1ft <- ref_extract(pri_062819_masked, shp = rows_2019_cen1ft, FUN = mean, buff = 0)
rowmean_pri_062819_2ft <- ref_extract(pri_062819_masked, shp = rows_2019_cen2ft, FUN = mean, buff = 0)
rowmean_pri_062819_3ft <- ref_extract(pri_062819_masked, shp = rows_2019_cen3ft, FUN = mean, buff = 0)
rowmean_pri_062819$Date <- as.Date("2019-06-28")
rowmean_pri_062819_1ft$Date <- as.Date("2019-06-28")
rowmean_pri_062819_2ft$Date <- as.Date("2019-06-28")
rowmean_pri_062819_3ft$Date <- as.Date("2019-06-28")
save.image("/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes/envir4.RData")

#combine them together
names(rowmean_pri_062819)[2] <- "PRI"
names(rowmean_pri_062819_1ft)[2] <- "PRI"
names(rowmean_pri_062819_2ft)[2] <- "PRI"
names(rowmean_pri_062819_3ft)[2] <- "PRI"
names(rowmean_pri_080219)[2] <- "PRI"
names(rowmean_pri_080219_1ft)[2] <- "PRI"
names(rowmean_pri_080219_2ft)[2] <- "PRI"
names(rowmean_pri_080219_3ft)[2] <- "PRI"
names(rowmean_pri_081019)[2] <- "PRI"
names(rowmean_pri_081019_1ft)[2] <- "PRI"
names(rowmean_pri_081019_2ft)[2] <- "PRI"
names(rowmean_pri_081019_3ft)[2] <- "PRI"
names(rowmean_pri_081519)[2] <- "PRI"
names(rowmean_pri_081519_1ft)[2] <- "PRI"
names(rowmean_pri_081519_2ft)[2] <- "PRI"
names(rowmean_pri_081519_3ft)[2] <- "PRI"
names(rowmean_pri_082219)[2] <- "PRI"
names(rowmean_pri_082219_1ft)[2] <- "PRI"
names(rowmean_pri_082219_2ft)[2] <- "PRI"
names(rowmean_pri_082219_3ft)[2] <- "PRI"



rowmean_pri <- rbind(rowmean_pri_062819, rowmean_pri_080219, rowmean_pri_081019, rowmean_pri_081519, rowmean_pri_082219)
rowmean_pri_1ft <- rbind(rowmean_pri_062819_1ft, rowmean_pri_080219_1ft, rowmean_pri_081019_1ft, rowmean_pri_081519_1ft, rowmean_pri_082219_1ft)
rowmean_pri_2ft <- rbind(rowmean_pri_062819_2ft, rowmean_pri_080219_2ft, rowmean_pri_081019_2ft, rowmean_pri_081519_2ft, rowmean_pri_082219_2ft)
rowmean_pri_3ft <- rbind(rowmean_pri_062819_3ft, rowmean_pri_080219_3ft, rowmean_pri_081019_3ft, rowmean_pri_081519_3ft, rowmean_pri_082219_3ft)

path_df_server <- "/z0/zt92/Tomato_biomass/tomato_analysis_2019/dataframes"
#path_df <- "C:/Users/zt92/Box Sync/BIOSTIMULANT FIELD SCREENING MASTER FOLDER/DRONE/macaw_pri/dataframes"
write.csv(rowmean_pri, file.path(path_df_server, "rowmean_pri.csv"), row.names = FALSE)
write.csv(rowmean_pri_1ft, file.path(path_df_server, "rowmean_pri_1ft.csv"), row.names = FALSE)
write.csv(rowmean_pri_2ft, file.path(path_df_server, "rowmean_pri_2ft.csv"), row.names = FALSE)
write.csv(rowmean_pri_3ft, file.path(path_df_server, "rowmean_pri_3ft.csv"), row.names = FALSE)

```

#Calculate useful vegetation indices
##Functions
```{r}
#Structure Indices 
NDVI <- function(macaw){
  red <- macaw$X670
  nir <- macaw$X800
  ndvi <- (nir-red)/(nir+red)
  return(ndvi)
}

RDVI <- function(macaw){
  red <- macaw$X670
  nir <- macaw$X800
  rdvi <- (nir-red)/(nir+red)^0.5
  return(rdvi)
}

#Chl Indices
MCARI <- function(macaw){
  x700 <- macaw$X700
  x670 <- macaw$X670
  x550 <- macaw$X550
  mcari <- ((x700-x670)-0.2*(x700-x550))*(x700/x670)
  return(mcari)
}

TCARI <- function(macaw){
  x700 <- macaw$X700
  x670 <- macaw$X670
  x550 <- macaw$X550
  tcari <- 3*((x700-x670)-0.2*(x700-x550)*(x700/x670))
  return(tcari)
}

TCARI.OSAVI <- function(macaw){
  x700 <- macaw$X700
  x670 <- macaw$X670
  x550 <- macaw$X550
  x800 <- macaw$X800
  tcari <- 3*((x700-x670)-0.2*(x700-x550)*(x700/x670))
  osavi <- ((1+0.16)*(x800-x670)/(x800+x670+0.16))
  tcari.osavi <- tcari/osavi
  return(tcari.osavi)
}

RER <- function(macaw){
  x700 <- macaw$X700
  x670 <- macaw$X670
  rer <- x700/x670
  return(rer)
}

#xanthophyll Indice

PRI <- function(macaw){
  x530 <- macaw$X530
  x570 <- macaw$X570
  pri <- (x530-x570)/(x530+x570)
  return(pri)
}

PRI550 <- function(macaw){
  x530 <- macaw$X530
  x550 <- macaw$X550
  pri550 <- (x530-x550)/(x530+x550)
  return(pri550)
}

PRInorm <- function(macaw){
  #pri
  x530 <- macaw$X530
  x570 <- macaw$X570
  pri <- (x530-x570)/(x530+x570)
  #rdvi
  red <- macaw$X670
  nir <- macaw$X800
  rdvi <- (nir-red)/(nir+red)^0.5
  #rer
  x700 <- macaw$X700
  x670 <- macaw$X670
  rer <- x700/x670
  #PRInorm
  prinorm <- pri/(rdvi*rer)
  return(prinorm)
}

PRInorm550 <- function(macaw){
  #pri550
  x530 <- macaw$X530
  x550 <- macaw$X550
  pri550 <- (x530-x550)/(x530+x550)
  #rdvi
  red <- macaw$X670
  nir <- macaw$X800
  rdvi <- (nir-red)/(nir+red)^0.5
  #rer
  x700 <- macaw$X700
  x670 <- macaw$X670
  rer <- x700/x670
  #PRInorm
  prinorm550 <- pri550/(rdvi*rer)
  return(prinorm550)
}

#Water Indices
WI <- function(macaw){
  x900 <- macaw$X900
  x970 <- macaw$X970
  wi <- x900/x970
  return(wi)
}

WI.NDVI <- function(macaw){
  x900 <- macaw$X900
  x970 <- macaw$X970
  wi <- x900/x970
  red <- macaw$X670
  nir <- macaw$X800
  ndvi <- (nir-red)/(nir+red)
  return(wi/ndvi)
}

```

##Apply the functions
###with vegetation mask
```{r}
#convert DN to reflectance
flagmean_macaw[,2:13] <- flagmean_macaw[,2:13]/65535
flagmean_macaw$ndvi <- NDVI(flagmean_macaw)
flagmean_macaw$pri <- PRI(flagmean_macaw)
flagmean_macaw$wi <- WI(flagmean_macaw)
flagmean_macaw$wi.ndvi <- WI.NDVI(flagmean_macaw)
flagmean_macaw$mcawi <- MCARI(flagmean_macaw)
flagmean_macaw$tcari.osavi <- TCARI.OSAVI(flagmean_macaw)
flagmean_macaw$tcari <- TCARI(flagmean_macaw)
flagmean_macaw$pri550 <- PRI550(flagmean_macaw)
flagmean_macaw$prinorm <- PRInorm(flagmean_macaw)
flagmean_macaw$prinorm550 <- PRInorm550(flagmean_macaw)
flagmean_macaw$rer <- RER(flagmean_macaw)
flagmean_macaw$rdvi <- RDVI(flagmean_macaw)fe


#output
write.csv(flagmean_macaw, file.path(path_df, "flagmean_macaw.csv"), row.names = FALSE)
write.csv(rowmean_macaw, file.path(path_df, "rowmean_macaw.csv"), row.names = FALSE)
write.csv(rowmean_macaw_1ft, file.path(path_df, "rowmean_macaw_1ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_2ft, file.path(path_df, "rowmean_macaw_2ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_3ft, file.path(path_df, "rowmean_macaw_3ft.csv"), row.names = FALSE)

```
###with fruti mask
```{r}
names(flagmean_macaw_exgexrmask)

flagmean_macaw_exgexrmask[,2:13] <- flagmean_macaw_exgexrmask[,2:13]/65535
flagmean_macaw_exgexrmask$ndvi <- NDVI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$pri <- PRI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$wi <- WI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$wi.ndvi <- WI.NDVI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$mcawi <- MCARI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$tcari.osavi <- TCARI.OSAVI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$tcari <- TCARI(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$pri550 <- PRI550(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$prinorm <- PRInorm(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$prinorm550 <- PRInorm550(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$rer <- RER(flagmean_macaw_exgexrmask)
flagmean_macaw_exgexrmask$rdvi <- RDVI(flagmean_macaw_exgexrmask)

path_df <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes"
write.csv(flagmean_macaw_exgexrmask, file.path(path_df, "flagmean_macaw_exgexrmask.csv"), row.names = FALSE)
```

#----------Read data from csv-------------------
#Read extracted csv files
```{r}
path_df <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes"
flagmean_macaw <- read.csv(file.path(path_df, "flagmean_macaw.csv"))
head(flagmean_macaw)
flagmean_macaw_exgexrmask <- read.csv(file.path(path_df, "flagmean_macaw_exgexrmask.csv"))
head(flagmean_macaw_exgexrmask)
#merge with the shapefile data to include the plant
path_shp <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/shapefiles"
#use the adjusted one
flagbuff_2019 <- shapefile(file.path(path_shp, "flags_tomato_2019_adj_buffer.shp"))
flagmean_macaw <- merge(flagmean_macaw, flagbuff_2019@data[,c("Row","id","Plant")], by = c("Row","id"))
flagmean_macaw_exgexrmask <- merge(flagmean_macaw_exgexrmask, flagbuff_2019@data[,c("Row","id","Plant")], by = c("Row","id"))
#remove 08-22 data
flagmean_macaw <- subs
et(flagmean_macaw, Date!="2019-08-22")
```
#Micasense vs MACAW
##Plot the trend of NDVI
```{r}
ggplot(flagmean_uav_nomask)
```


#Ground Measurements
##Read SWP 
```{r}
path_swp <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/PHYSIOLOGICAL DATA/SWP"
files_swp <- list.files(path_swp, full.names = TRUE)
list_swp <- list()
for(i in 1:length(files_swp)){
  temp_df <- read_xlsx(files_swp[i])[,1:5]
  list_swp[[i]] <- temp_df
}
files_swp
names(list_swp) <- c("2019-05-31","2019-06-11","2019-06-26","2019-07-17","2019-07-25","2019-08-01","2019-08-08","2019-08-14")

#Add date column 
for(i in 1:length(list_swp)){
  list_swp[[i]]$Date <- as.Date(names(list_swp)[i])
}
list_swp[[8]]

#rbind them together
swp_PL <- do.call(rbind, list_swp)
head(swp_PL)
tail(swp_PL)

names(flagmean_macaw)
#change names 
names(swp_PL) <- c("Block","Plot","Treatment","Plant","SWP", "Date")

#aggregate by row
class(swp_PL$SWP)
swp_PL$SWP <- as.numeric(swp_PL$SWP)
sum(is.na(swp_PL$SWP))
dim(swp_PL)  #1070, 6

rowflagmean_swp <- aggregate(swp_PL$SWP, by = list("Block"=swp_PL$Block, "Plot"=swp_PL$Plot, "Treatment"=swp_PL$Treatment, "Date"=swp_PL$Date), FUN = function(x){mean(x, na.rm=TRUE)})
names(rowflagmean_swp)[5] <- "SWP"
#rowflagmean_macaw_swp <- aggregate(swp_PL$SWP, by = list("Block"=swp_PL$Block, "Plot"=swp_PL$Plot, "Treatment"=swp_PL$Treatment, "Date"=swp_PL$Date), FUN = function(x){mean(x, na.rm=TRUE)})
#names(rowflagmean_macaw_swp)[5] <- "SWP"

sum(is.na(rowflagmean_macaw_swp$x))
dim(rowflagmean_macaw_swp) #140, 6

```
##Read LiCOR
```{r}
path_licor <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes/Physiology_Measurement/LICOR"
files_licor <- list.files(path_licor, full.names = TRUE)
files_licor
list_licor <- list()

for(i in 1:length(files_licor)){
  temp_df <- read_xlsx(files_licor[i], sheet = "COMBINED")[,c("Block","Treatment","Plot","Plant.Num","Photo","Cond")]
  list_licor[[i]] <- temp_df
}
names(list_licor) <- c("2019-05-31","2019-06-11","2019-06-26","2019-07-17","2019-07-25","2019-08-01","2019-08-08","2019-08-14")
for(i in 1:length(list_licor)){
  list_licor[[i]]$Date <- as.Date(names(list_licor)[i])
}
licor_PL <- do.call(rbind, list_licor)

names(licor_PL)
names(licor_PL)[4] <- "Plant"

rowflagmean_licor <- aggregate(licor_PL[5:6], by = list("Block"=licor_PL$Block, "Plot"=licor_PL$Plot, "Treatment"=licor_PL$Treatment, "Date"=licor_PL$Date), FUN = function(x){mean(x, na.rm=TRUE)})
#rowflagmean_macaw_swp <- aggregate(swp_PL$SWP, by = list("Block"=swp_PL$Block, "Plot"=swp_PL$Plot, "Treatment"=swp_PL$Treatment, "Date"=swp_PL$Date), FUN = function(x){mean(x, na.rm=TRUE)})
#sum(is.na(rowflagmean_macaw_swp$x))
#dim(rowflagmean_macaw_swp) #140, 6
#names(rowflagmean_macaw_swp)[5] <- "SWP"

```
##Read Chlorophyll
```{r}
path_chl <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes/Physiology_Measurement/CHL"
files_chl <- list.files(path_chl, full.names = TRUE)
files_chl
list_chl <- list()
for(i in 1:length(files_chl)){
  temp_df <- read_xlsx(files_chl[i], sheet = 1)[,c("PLOT","TREATMENT","PLANT","CHL")]
  list_chl[[i]] <- temp_df
}
names(list_chl) <- c("2019-05-31","2019-06-11","2019-06-25","2019-06-26","2019-07-17","2019-07-25","2019-08-01","2019-08-08","2019-08-14")

for(i in 1:length(list_chl)){
  list_chl[[i]]$Date <- as.Date(names(list_chl)[i])
}
chl_PL <- do.call(rbind, list_chl)
names(chl_PL) <- c("Plot","Treatment","Plant","CHL","Date")
```
##Read IRT
```{r}
path_irt <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes/Physiology_Measurement/IRT"
files_irt <- list.files(path_irt, full.names = TRUE)
files_irt
list_irt <- list()
for(i in 1:length(files_irt)){
  temp_df <- read_xlsx(files_irt[i], sheet = 1)[,c("PLOT","TREATMENT","PLANT","TEMP","EDITED TIME")]
  list_irt[[i]] <- temp_df
}
names(list_irt) <- c("2019-05-31","2019-06-11","2019-06-25","2019-06-25","2019-06-26","2019-07-17","2019-07-25","2019-08-01","2019-08-08","2019-08-14")
for(i in 1:length(list_irt)){
  list_irt[[i]]$Date <- as.Date(names(list_irt)[i])
}
irt_PL <- do.call(rbind, list_irt)
names(irt_PL) <- c("Plot","Treatment","Plant","IRT","MeasureTime","Date")
```
##Combine ground measurement together
```{r}
phys_PL <- merge(swp_PL, licor_PL, by = c("Block","Plot","Treatment","Plant","Date"))
#phys_PL <- merge(phys_PL, chl_PL, by = c("Plot","Treatment","Plant","Date"))
#phys_PL <- merge(phys_PL, irt_PL, by = c("Plot","Treatment","Plant","Date"))
dim(phys_PL)
sum(is.na(phys_PL))
View(phys_PL)

phys_PL <- merge(irt_PL, chl_PL, by = c("Plot","Treatment","Plant","Date"))
head(phys_PL)
dim(phys_PL)  #1360

phys_PL <- merge(phys_PL, licor_PL, by = c("Plot","Treatment","Plant","Date"))
head(phys_PL)
dim(phys_PL)  #1126

phys_PL <- merge(phys_PL, swp_PL, by = c("Block","Plot","Treatment","Plant","Date"))
head(phys_PL)
dim(phys_PL)  #1101
```
##Combine with macaw data
```{r}
#flagmean_macaw$Date <- as.Date(flagmean_macaw$Date)
#unique(flagmean_macaw$Date)
flagmean_macaw_exgexrmask$Date <- as.Date(flagmean_macaw_exgexrmask$Date)
unique(flagmean_macaw_exgexrmask$Date)
unique(phys_PL$Date)

for(i in 1:dim(phys_PL)[1]){
  if(phys_PL[i,]$Date=="2019-06-26"){
    phys_PL[i,]$Date= "2019-06-28"
  }
  if(phys_PL[i,]$Date=="2019-08-01"){
    phys_PL[i,]$Date="2019-08-02"
  }
  if(phys_PL[i,]$Date=="2019-08-14"){
    phys_PL[i,]$Date="2019-08-15"
  }
}

phys_PL$Block <- as.character(phys_PL$Block)
flagmean_macaw_exgexrmask_phys <- base::merge(flagmean_macaw_exgexrmask, phys_PL, by = c("Block","Treatment","Plant","Date"))
head(flagmean_macaw_exgexrmask_phys)
dim(flagmean_macaw_exgexrmask_phys)  #315, 40
dim(subset(flagmean_macaw_exgexrmask_phys, Date=="2019-06-28"))  #120,40
dim(subset(flagmean_macaw_exgexrmask_phys, Date=="2019-08-02")) #120,40
dim(subset(flagmean_macaw_exgexrmask_phys, Date=="2019-08-15")) #75, 40, this is because the phys data only contains 75 rows 


#flagmean_macaw_phys <- base::merge(flagmean_macaw, phys_PL, by = c("Block","Treatment","Plant","Date"))
head(flagmean_macaw_phys)
dim(flagmean_macaw_phys)  #315, 28
unique(flagmean_macaw_phys$Date)  
dim(subset(flagmean_macaw_phys, Date=="2019-06-28"))  #120
dim(subset(flagmean_macaw_phys, Date=="2019-08-02")) #120
dim(subset(flagmean_macaw_phys, Date=="2019-08-15")) #75

View(subset(flagmean_macaw_phys, Date=="2019-06-28"))
head(flagmean_macaw_phys)

#change classes
##veg mask
flagmean_macaw_phys$Block <- as.factor(flagmean_macaw_phys$Block)
flagmean_macaw_phys$Plant <- as.factor(as.character(flagmean_macaw_phys$Plant))
flagmean_macaw_phys$Plot <- as.factor(flagmean_macaw_phys$Plot)
flagmean_macaw_phys$SWP <- as.numeric(flagmean_macaw_phys$SWP)
flagmean_macaw_phys$CHL <- as.numeric(flagmean_macaw_phys$CHL)
##fruit mask
flagmean_macaw_exgexrmask_phys$Block <- as.factor(flagmean_macaw_exgexrmask_phys$Block)
flagmean_macaw_exgexrmask_phys$Plant <- as.factor(as.character(flagmean_macaw_exgexrmask_phys$Plant))
flagmean_macaw_exgexrmask_phys$Plot <- as.factor(flagmean_macaw_exgexrmask_phys$Plot)
flagmean_macaw_exgexrmask_phys$SWP <- as.numeric(flagmean_macaw_exgexrmask_phys$SWP)
flagmean_macaw_exgexrmask_phys$CHL <- as.numeric(flagmean_macaw_exgexrmask_phys$CHL)

```
###Only SWP
```{r}
#flagmean_macaw$Date <- as.Date(flagmean_macaw$Date)
#unique(flagmean_macaw$Date)
flagmean_macaw_exgexrmask$Date <- as.Date(flagmean_macaw_exgexrmask$Date)
unique(flagmean_macaw_exgexrmask$Date)
unique(swp_PL$Date)

for(i in 1:dim(swp_PL)[1]){
  if(swp_PL[i,]$Date=="2019-06-26"){
    swp_PL[i,]$Date= "2019-06-28"
  }
  if(swp_PL[i,]$Date=="2019-08-01"){
    swp_PL[i,]$Date="2019-08-02"
  }
  if(swp_PL[i,]$Date=="2019-08-14"){
    swp_PL[i,]$Date="2019-08-15"
  }
}

swp_PL$Block <- as.character(swp_PL$Block)
flagmean_macaw_exgexrmask_swp <- base::merge(flagmean_macaw_exgexrmask, swp_PL, by = c("Block","Treatment","Plant","Date"))
head(flagmean_macaw_exgexrmask_swp)
dim(flagmean_macaw_exgexrmask_swp)  #315, 40
dim(subset(flagmean_macaw_exgexrmask_swp, Date=="2019-06-28"))  #120,40
dim(subset(flagmean_macaw_exgexrmask_swp, Date=="2019-08-02")) #120,40
dim(subset(flagmean_macaw_exgexrmask_swp, Date=="2019-08-15")) #90, 35

#flagmean_macaw_swp <- base::merge(flagmean_macaw, swp_PL, by = c("Block","Treatment","Plant","Date"))
head(flagmean_macaw_swp)
dim(flagmean_macaw_swp)  #315, 28
unique(flagmean_macaw_swp$Date)  
dim(subset(flagmean_macaw_swp, Date=="2019-06-28"))  #120
dim(subset(flagmean_macaw_swp, Date=="2019-08-02")) #120
dim(subset(flagmean_macaw_swp, Date=="2019-08-15")) #75

View(subset(flagmean_macaw_swp, Date=="2019-06-28"))
head(flagmean_macaw_swp)

#change classes
##veg mask
flagmean_macaw_swp$Block <- as.factor(flagmean_macaw_swp$Block)
flagmean_macaw_swp$Plant <- as.factor(as.character(flagmean_macaw_swp$Plant))
flagmean_macaw_swp$Plot <- as.factor(flagmean_macaw_swp$Plot)
flagmean_macaw_swp$SWP <- as.numeric(flagmean_macaw_swp$SWP)
#flagmean_macaw_swp$CHL <- as.numeric(flagmean_macaw_swp$CHL)
##fruit mask
flagmean_macaw_exgexrmask_swp$Block <- as.factor(flagmean_macaw_exgexrmask_swp$Block)
flagmean_macaw_exgexrmask_swp$Plant <- as.factor(as.character(flagmean_macaw_exgexrmask_swp$Plant))
flagmean_macaw_exgexrmask_swp$Plot <- as.factor(flagmean_macaw_exgexrmask_swp$Plot)
flagmean_macaw_exgexrmask_swp$SWP <- as.numeric(flagmean_macaw_exgexrmask_swp$SWP)
#flagmean_macaw_exgexrmask_swp$CHL <- as.numeric(flagmean_macaw_exgexrmask_swp$CHL)

```

#Add some indices
```{r}

flagmean_macaw_phys$ndvi <- NDVI(flagmean_macaw_phys)
flagmean_macaw_phys$pri <- PRI(flagmean_macaw_phys)
flagmean_macaw_phys$wi <- WI(flagmean_macaw_phys)
flagmean_macaw_phys$wi.ndvi <- WI.NDVI(flagmean_macaw_phys)
flagmean_macaw_phys$mcawi <- MCARI(flagmean_macaw_phys)
flagmean_macaw_phys$tcari.osavi <- TCARI.OSAVI(flagmean_macaw_phys)
flagmean_macaw_phys$tcari <- TCARI(flagmean_macaw_phys)
flagmean_macaw_phys$pri550 <- PRI550(flagmean_macaw_phys)
flagmean_macaw_phys$prinorm <- PRInorm(flagmean_macaw_phys)
flagmean_macaw_phys$prinorm550 <- PRInorm550(flagmean_macaw_phys)
flagmean_macaw_phys$rer <- RER(flagmean_macaw_phys)
flagmean_macaw_phys$rdvi <- RDVI(flagmean_macaw_phys)

```

#Exploratory Plots
##Boxplot & scatterplot
###veg mask 
```{r}
flagmean_macaw_phys$Treatment2 <- factor(flagmean_macaw_phys$Treatment, levels = c("BAYER 16 (SOIL) WW", "CONTROL WW", "CONTROL DDD"), order = TRUE)

#SWP change
ggplot(flagmean_macaw_phys, aes(x = as.factor(Date), y = -SWP, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("Stem Water Potential (Bars)") + scale_fill_tableau() + ggtitle("Stem Water Potential Seasonal Change")

#PRI change
ggplot(flagmean_macaw_phys, aes(x = as.factor(Date), y = pri, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("PRI") + scale_fill_tableau() + ggtitle("PRI")

#NDVI 
ggplot(flagmean_macaw_phys, aes(x = as.factor(Date), y = NDVI, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("NDVI") + scale_fill_tableau() + ggtitle("NDVI")

#TCARI.OSAVI
ggplot(flagmean_macaw_phys, aes(x = as.factor(Date), y = tcari.osavi, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("TCARI/OSAVI") + scale_fill_tableau() + ggtitle("TCARI/OSAVI")

#WI
ggplot(flagmean_macaw_phys, aes(x = as.factor(Date), y = wi, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("WI") + scale_fill_tableau() + ggtitle("WI")


##SWP change
ggplot(flagmean_macaw_phys, aes(x = Date, y = -SWP, color = Treatment)) + geom_point()
flagmean_macaw_phys
lm1 <- lm(flagmean_macaw_phys$SWP ~ flagmean_macaw_phys$pri + flagmean_macaw_phys$Treatment)
anova(lm1)

##Cond
ggplot(flagmean_macaw_phys, aes(x = Date, y = Cond, color = Treatment)) + geom_point()

##Chl
ggplot(flagmean_macaw_phys, aes(x = Date, y = CHL, color = Treatment)) + geom_point()

##PRI change
ggplot(flagmean_macaw_phys, aes(x = Date, y = pri, color = Treatment)) + geom_point() + ylab("PRI")

##NDVI change
ggplot(flagmean_macaw_phys, aes(x = Date, y = ndvi, color = Treatment)) + geom_point() + ylab("NDVI")

##TCARI.OSAVI
ggplot(flagmean_macaw_phys, aes(x = Date, y = tcari.osavi, color = Treatment)) + geom_point() + ylab("TCARI/OSAVI")

##wi
ggplot(flagmean_macaw_phys, aes(x = Date, y = wi, color = Treatment)) + geom_point() + ylab("WI")

##wi.ndvi
ggplot(flagmean_macaw_phys, aes(x = Date, y = wi.ndvi, color = Treatment)) + geom_point() + ylab("WI/NDVI")

##mcari
ggplot(flagmean_macaw_phys, aes(x = Date, y = mcari, color = Treatment)) + geom_point() + ylab("MCARI")

#TCARI.OSAVI vs CHL
ggplot(flagmean_macaw_phys, aes(x = CHL, y = tcari.osavi/ndvi, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("TCARI/OSAVI") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = tcari.osavi, y = CHL)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm")


##PRI vs SWP
ggplot(flagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point() + xlab("PRI from MACAW") + ylab("SWP") + geom_smooth(method = "lm")+ facet_wrap(~Date, scale = "free", nrow = 2)+ theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "none")+theme(legend.title = element_blank())


ggplot(flagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
cor(flagmean_macaw_phys$pri, flagmean_macaw_phys$SWP)^2  #0.376
lm1 <- lm(pri~SWP, data = flagmean_macaw_phys)
summary(lm1)
ggplot(flagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(flagmean_macaw_phys, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$pri/flagmean_macaw_phys$ndvi, flagmean_macaw_phys$SWP)^2  #0.387
#The difference is due to the 

##PRI550
ggplot(flagmean_macaw_phys, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$pri550, flagmean_macaw_phys$SWP)^2  #0.0149

##PRInorm
###SWP
ggplot(flagmean_macaw_phys, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$prinorm, flagmean_macaw_phys$SWP)^2  #0.2703
###Cond
ggplot(flagmean_macaw_phys, aes(x = prinorm, y = Cond, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = prinorm, y = Cond)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$prinorm, flagmean_macaw_phys$Cond)^2  #0.004


##PRI550norm
ggplot(flagmean_macaw_phys, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$prinorm550, flagmean_macaw_phys$SWP)^2  #0.0788

##WI
ggplot(flagmean_macaw_phys, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(flagmean_macaw_phys$wi, flagmean_macaw_phys$SWP)^2  #0.4004
ggplot(flagmean_macaw_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())


##WI/NDVI
ggplot(flagmean_macaw_phys, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$wi.ndvi, flagmean_macaw_phys$SWP)^2  #0.2169

#Chlorophyll Index
##RER
ggplot(flagmean_macaw_phys, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$rer, flagmean_macaw_phys$SWP)^2  #0.024
##TCARI
ggplot(flagmean_macaw_phys, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$tcari, flagmean_macaw_phys$SWP)^2  #0.387
##TCARI.OSAVI
ggplot(flagmean_macaw_phys, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$tcari.osavi, flagmean_macaw_phys$SWP)^2  #0.3349
##MCARI
ggplot(flagmean_macaw_phys, aes(x = mcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = mcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$mcari, flagmean_macaw_phys$SWP)^2  #0.292

#Strucutre Index
##NDVI
ggplot(flagmean_macaw_phys, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$ndvi, flagmean_macaw_phys$SWP)^2  #0.1849
##RDVI
ggplot(flagmean_macaw_phys, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$rdvi, flagmean_macaw_phys$SWP)^2  #0.324684





##PRI/(RDVI*TCARI)
ggplot(flagmean_macaw_phys, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") + xlim(-1.5,0)
ggplot(flagmean_macaw_phys, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")+xlim(-1.5, 0)
cor(flagmean_macaw_phys$pri/(flagmean_macaw_phys$rdvi*flagmean_macaw_phys$tcari), flagmean_macaw_phys$SWP)^2  #0.068



##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$pri/(flagmean_macaw_phys$ndvi*flagmean_macaw_phys$tcari.osavi), flagmean_macaw_phys$SWP)^2  #0.068

##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_phys, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys$pri/(flagmean_macaw_phys$ndvi*flagmean_macaw_phys$tcari), flagmean_macaw_phys$SWP)^2  #0.068


```
###fruit mask
```{r}
flagmean_macaw_exgexrmask_phys$Treatment2 <- factor(flagmean_macaw_exgexrmask_phys$Treatment, levels = c("BAYER 16 (SOIL) WW", "CONTROL WW", "CONTROL DDD"), order = TRUE)

#SWP change
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = -SWP, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("Stem Water Potential (Bars)") + scale_fill_tableau() + ggtitle("Stem Water Potential Seasonal Change")
#stomatal conductance
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = Cond, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("Stomatal Conductance") + scale_fill_tableau() + ggtitle("Stomatal Conductance")


#PRI change
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = pri, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("PRI") + scale_fill_tableau() + ggtitle("PRI")

#NDVI 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = NDVI, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("NDVI") + scale_fill_tableau() + ggtitle("NDVI")

#TCARI.OSAVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = tcari.osavi, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("TCARI/OSAVI") + scale_fill_tableau() + ggtitle("TCARI/OSAVI")

#WI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = as.factor(Date), y = wi, fill = Treatment2)) + geom_boxplot(position = position_dodge(0.75))  + theme_pubr(base_size = 14, base_family = "serif", border = TRUE, legend = "right")+  xlab("Date") + ylab("WI") + scale_fill_tableau() + ggtitle("WI")


##SWP change
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = -SWP, color = Treatment)) + geom_point()
flagmean_macaw_exgexrmask_phys
lm1 <- lm(flagmean_macaw_exgexrmask_phys$SWP ~ flagmean_macaw_exgexrmask_phys$pri + flagmean_macaw_exgexrmask_phys$Treatment)
anova(lm1)

##Cond
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = Cond, color = Treatment)) + geom_point()

##Chl
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = CHL, color = Treatment)) + geom_point()

##PRI change
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = pri, color = Treatment)) + geom_point() + ylab("PRI")

##NDVI change
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = ndvi, color = Treatment)) + geom_point() + ylab("NDVI")

##TCARI.OSAVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = tcari.osavi, color = Treatment)) + geom_point() + ylab("TCARI/OSAVI")

##wi
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = wi, color = Treatment)) + geom_point() + ylab("WI")

##wi.ndvi
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = wi.ndvi, color = Treatment)) + geom_point() + ylab("WI/NDVI")

##mcari
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = Date, y = mcari, color = Treatment)) + geom_point() + ylab("MCARI")

#TCARI.OSAVI vs CHL
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = CHL, y = tcari.osavi/ndvi, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("TCARI/OSAVI") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = tcari.osavi, y = CHL)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm")


##PRI vs SWP
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point() + xlab("PRI from MACAW") + ylab("SWP") + geom_smooth(method = "lm")+ facet_wrap(~Date, scale = "free", nrow = 2)+ theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "none")+theme(legend.title = element_blank())


ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
cor(flagmean_macaw_exgexrmask_phys$pri, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.376
lm1 <- lm(pri~SWP, data = flagmean_macaw_exgexrmask_phys)
summary(lm1)
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$pri/flagmean_macaw_exgexrmask_phys$ndvi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.387
#The difference is due to the 

##PRI550
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$pri550, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.0149

##PRInorm
###SWP
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$prinorm, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.2703
###Cond
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = Cond, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = Cond)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$prinorm, flagmean_macaw_exgexrmask_phys$Cond)^2  #0.004


##PRI550norm
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$prinorm550, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.0788

##WI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(flagmean_macaw_exgexrmask_phys$wi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.4004
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())


##WI/NDVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$wi.ndvi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.2169

#Chlorophyll Index
##RER
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$rer, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.024
##TCARI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$tcari, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.387
##TCARI.OSAVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$tcari.osavi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.3349
##MCARI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = mcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = mcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$mcari, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.292

#Strucutre Index
##NDVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$ndvi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.1849
##RDVI
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$rdvi, flagmean_macaw_exgexrmask_phys$SWP)^2  #0.324684





##PRI/(RDVI*TCARI)
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") + xlim(-1.5,0)
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")+xlim(-1.5, 0)
cor(flagmean_macaw_exgexrmask_phys$pri/(flagmean_macaw_exgexrmask_phys$rdvi*flagmean_macaw_exgexrmask_phys$tcari), flagmean_macaw_exgexrmask_phys$SWP)^2  #0.068



##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$pri/(flagmean_macaw_exgexrmask_phys$ndvi*flagmean_macaw_exgexrmask_phys$tcari.osavi), flagmean_macaw_exgexrmask_phys$SWP)^2  #0.068

##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_exgexrmask_phys$pri/(flagmean_macaw_exgexrmask_phys$ndvi*flagmean_macaw_exgexrmask_phys$tcari), flagmean_macaw_exgexrmask_phys$SWP)^2  #0.068


```

##Spectral reflectance of different treatment 
###veg mask 
```{r}
unique(flagmean_macaw$Date)
flagmean_macaw_062819 <- subset(flagmean_macaw, Date=="2019-06-28")
flagmean_macaw_080219 <- subset(flagmean_macaw, Date=="2019-08-02")
flagmean_macaw_081519 <- subset(flagmean_macaw, Date=="2019-08-15")
flagmean_macaw_082219 <- subset(flagmean_macaw, Date=="2019-08-22")
names(flagmean_macaw)
wavelen_macaw <- c(450, 480, 530, 550, 570, 670, 700, 720, 740, 800, 900, 970)

ref_flagmean <- gather(flagmean_macaw, wavelen, reflectance, X800:X970, factor_key = FALSE)
#change wavelen to numeric
ref_flagmean$wavelen <- as.numeric(substring(ref_flagmean$wavelen,2))
unique(ref_flagmean$wavelen)

#subset by date
ref_flagmean_062819 <- subset(ref_flagmean, Date=="2019-06-28")
ref_flagmean_080219 <- subset(ref_flagmean, Date=="2019-08-02")
ref_flagmean_081519 <- subset(ref_flagmean, Date=="2019-08-15")
ref_flagmean_082219 <- subset(ref_flagmean, Date=="2019-08-22")

#calculate mean and variance
ref_flagmean_062819_sum <- ref_flagmean_062819 %>% group_by(Treatment, wavelen) %>% summarise(Mean = mean(reflectance), Var = var(reflectance))
ref_flagmean_080219_sum <- ref_flagmean_080219 %>% group_by(Treatment, wavelen) %>% summarise(Mean = mean(reflectance), Var = var(reflectance))
ref_flagmean_081519_sum <- ref_flagmean_081519 %>% group_by(Treatment, wavelen) %>% summarise(Mean = mean(reflectance), Var = var(reflectance))
ref_flagmean_082219_sum <- ref_flagmean_082219 %>% group_by(Treatment, wavelen) %>% summarise(Mean = mean(reflectance), Var = var(reflectance))



#Plot
ggplot(ref_flagmean_062819_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line(size = 1) + xlab("Wavelength(nm)")+ylab("Average Reflectance") + ggtitle("2019-06-28") + theme_pubr(border  =TRUE, base_family = "serif", base_size = 14, legend = "right") + ylim(0,0.6) #+ geom_errorbar(aes(x = wavelen, ymin =  Mean - Var, ymax = Mean + Var, color = Treatment))
ggplot(ref_flagmean_080219_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line(size = 1) + xlab("Wavelength(nm)")+ylab("Average Reflectance") + ggtitle("2019-08-02")+ theme_pubr(border  =TRUE, base_family = "serif", base_size = 14, legend = "right") + ylim(0,0.6)#+ geom_errorbar(aes(x = wavelen, ymin =  Mean - Var, ymax = Mean + Var, color = Treatment))
ggplot(ref_flagmean_081519_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line(size = 1) + xlab("Wavelength(nm)")+ylab("Average Reflectance") + ggtitle("2019-08-15")+ theme_pubr(border  =TRUE, base_family = "serif", base_size = 14, legend = "right") + ylim(0,0.6) #+ geom_errorbar(aes(x = wavelen, ymin =  Mean - Var, ymax = Mean + Var, color = Treatment))
ggplot(ref_flagmean_081519_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line(size = 1) + xlab("Wavelength(nm)")+ylab("Average Reflectance") + ggtitle("2019-08-15") + xlim(450, 800)+ theme_pubr(border  =TRUE, base_family = "serif", base_size = 14, legend = "right") #+ geom_errorbar(aes(x = wavelen, ymin =  Mean - Var, ymax = Mean + Var, color = Treatment))

#ggplot(ref_flagmean_082219_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line(size = 1) + xlab("Wavelength(nm)")+ylab("Average Reflectance") + ggtitle("2019-08-22") #+ geom_errorbar(aes(x = wavelen, ymin =  Mean - Var, ymax = Mean + Var, color = Treatment))

#ggplot(ref_flagmean_062819, aes(x = wavelen, y = reflectance, color = Treatment)) + geom_line(alpha = 0.2, size = 0.2)+ ylab("Average Reflectance")+xlab("Wavelength")#+ geom_line(data = ref_flagmean_062819_sum, aes(x = wavelen, y = Mean, color = Treatment))
#ggplot(ref_flagmean_062819_sum, aes(x = wavelen, y = Mean, color = Treatment)) + geom_line()+ylab("Average Reflectance")+xlab("Wavelength(nm)") 



ggplot(subset(ref_flagmean, Date=="2019-08-02"), aes(x = wavelen, y = reflectance, color = Treatment)) + geom_point() 
head(ref_flagmean)
ref_flagmean_080219 <- data.frame(wavelen = wavelen_macaw, ref = flagmean_macaw_081519[,c])
plot(x = wavelen_macaw, y =  flagmean_macaw_081519[,c(5:15,4)], color = flagmean_macaw_081519$Treatment)

```

##Only 06-28 and 08-02
```{r}
flagmean_macaw_phys2 <- subset(flagmean_macaw_phys, Date!="2019-08-15")
dim(flagmean_macaw_phys2) #240, 41

##PRI vs SWP
ggplot(flagmean_macaw_phys2, aes(x = pri, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
cor(flagmean_macaw_phys2$pri, flagmean_macaw_phys2$SWP)^2  #0.117
lm1 <- lm(pri~SWP, data = flagmean_macaw_phys2)
summary(lm1)
ggplot(flagmean_macaw_phys2, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(flagmean_macaw_phys2, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$pri/flagmean_macaw_phys2$ndvi, flagmean_macaw_phys2$SWP)^2  #0.387
#The difference is due to the 

##PRI550
ggplot(flagmean_macaw_phys2, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$pri550, flagmean_macaw_phys2$SWP)^2  #0.0149

##PRInorm
###SWP
ggplot(flagmean_macaw_phys2, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$prinorm, flagmean_macaw_phys2$SWP)^2  #0.2703
###Cond
ggplot(flagmean_macaw_phys2, aes(x = prinorm, y = Cond, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = prinorm, y = Cond)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$prinorm, flagmean_macaw_phys2$Cond)^2  #0.004


##PRI550norm
ggplot(flagmean_macaw_phys2, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$prinorm550, flagmean_macaw_phys2$SWP)^2  #0.0788

##WI
ggplot(flagmean_macaw_phys2, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(flagmean_macaw_phys2$wi, flagmean_macaw_phys2$SWP)^2  #0.4004
ggplot(flagmean_macaw_phys2, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())


##WI/NDVI
ggplot(flagmean_macaw_phys2, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$wi.ndvi, flagmean_macaw_phys2$SWP)^2  #0.2169

#Chlorophyll Index
##RER
ggplot(flagmean_macaw_phys2, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$rer, flagmean_macaw_phys2$SWP)^2  #0.024
##TCARI
ggplot(flagmean_macaw_phys2, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$tcari, flagmean_macaw_phys2$SWP)^2  #0.387
##TCARI.OSAVI
ggplot(flagmean_macaw_phys2, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$tcari.osavi, flagmean_macaw_phys2$SWP)^2  #0.3349
##MCARI
ggplot(flagmean_macaw_phys2, aes(x = mcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = mcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$mcari, flagmean_macaw_phys2$SWP)^2  #0.292

#Strucutre Index
##NDVI
ggplot(flagmean_macaw_phys2, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$ndvi, flagmean_macaw_phys2$SWP)^2  #0.1849
##RDVI
ggplot(flagmean_macaw_phys2, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$rdvi, flagmean_macaw_phys2$SWP)^2  #0.324684





##PRI/(RDVI*TCARI)
ggplot(flagmean_macaw_phys2, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") + xlim(-1.5,0)
ggplot(flagmean_macaw_phys2, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")+xlim(-1.5, 0)
cor(flagmean_macaw_phys2$pri/(flagmean_macaw_phys2$rdvi*flagmean_macaw_phys2$tcari), flagmean_macaw_phys2$SWP)^2  #0.068



##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_phys2, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$pri/(flagmean_macaw_phys2$ndvi*flagmean_macaw_phys2$tcari.osavi), flagmean_macaw_phys2$SWP)^2  #0.068

##PRI/(NDVI*TCARI)
ggplot(flagmean_macaw_phys2, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(flagmean_macaw_phys2, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(flagmean_macaw_phys2$pri/(flagmean_macaw_phys2$ndvi*flagmean_macaw_phys2$tcari), flagmean_macaw_phys2$SWP)^2  #0.068

```
#Aggregate by row
##veg mask 
```{r}
rowflagmean_macaw_phys <- aggregate(flagmean_macaw_phys[,c(8:19,22:33,35:39)], by = list("Row"=flagmean_macaw_phys$Row, "Treatment"=flagmean_macaw_phys$Treatment, "Block"=flagmean_macaw_phys$Block, "Date"=flagmean_macaw_phys$Date), FUN = mean)
rowflagmean_macaw_phys2 <- subset(rowflagmean_macaw_phys, Date!="2019-08-15")

##PRI vs SWP
ggplot(rowflagmean_macaw_phys, aes(x = pri, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
ggplot(rowflagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point() + xlab("PRI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")

##PRI vs Cond
ggplot(rowflagmean_macaw_phys, aes(x = pri, y = Cond)) + geom_point() + xlab("PRI from MACAW") + ylab("Stomatal Conductance") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")


cor(rowflagmean_macaw_phys$pri, rowflagmean_macaw_phys$SWP)^2  #0.376
lm1 <- lm(pri~SWP, data = rowflagmean_macaw_phys)
summary(lm1)
ggplot(rowflagmean_macaw_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(rowflagmean_macaw_phys, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$pri/rowflagmean_macaw_phys$ndvi, rowflagmean_macaw_phys$SWP)^2  #0.387
#The difference is due to the 

##PRI550
ggplot(rowflagmean_macaw_phys, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$pri550, rowflagmean_macaw_phys$SWP)^2  #0.0149

##PRInorm
###SWP
ggplot(rowflagmean_macaw_phys, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$prinorm, rowflagmean_macaw_phys$SWP)^2  #0.2703
###Cond
ggplot(rowflagmean_macaw_phys, aes(x = prinorm, y = Cond, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = prinorm, y = Cond)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$prinorm, rowflagmean_macaw_phys$Cond)^2  #0.004


##PRI550norm
ggplot(rowflagmean_macaw_phys, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$prinorm550, rowflagmean_macaw_phys$SWP)^2  #0.0788

##WI
ggplot(rowflagmean_macaw_phys, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(rowflagmean_macaw_phys$wi, rowflagmean_macaw_phys$SWP)^2  #0.4004
ggplot(rowflagmean_macaw_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())


##WI/NDVI
ggplot(rowflagmean_macaw_phys, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$wi.ndvi, rowflagmean_macaw_phys$SWP)^2  #0.2169

#Chlorophyll Index
##RER
ggplot(rowflagmean_macaw_phys, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$rer, rowflagmean_macaw_phys$SWP)^2  #0.024
##TCARI
ggplot(rowflagmean_macaw_phys, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$tcari, rowflagmean_macaw_phys$SWP)^2  #0.387
##TCARI.OSAVI
ggplot(rowflagmean_macaw_phys, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$tcari.osavi, rowflagmean_macaw_phys$SWP)^2  #0.3349
##MCARI
ggplot(rowflagmean_macaw_phys, aes(x = mcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = mcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$mcari, rowflagmean_macaw_phys$SWP)^2  #0.292

#Strucutre Index
##NDVI
ggplot(rowflagmean_macaw_phys, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$ndvi, rowflagmean_macaw_phys$SWP)^2  #0.1849
##RDVI
ggplot(rowflagmean_macaw_phys, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$rdvi, rowflagmean_macaw_phys$SWP)^2  #0.324684





##PRI/(RDVI*TCARI)
ggplot(rowflagmean_macaw_phys, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") + xlim(-1.5,0)
ggplot(rowflagmean_macaw_phys, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")+xlim(-1.5, 0)
cor(rowflagmean_macaw_phys$pri/(rowflagmean_macaw_phys$rdvi*rowflagmean_macaw_phys$tcari), rowflagmean_macaw_phys$SWP)^2  #0.068



##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$pri/(rowflagmean_macaw_phys$ndvi*rowflagmean_macaw_phys$tcari.osavi), rowflagmean_macaw_phys$SWP)^2  #0.068

##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_phys, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_phys, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_phys$pri/(rowflagmean_macaw_phys$ndvi*rowflagmean_macaw_phys$tcari), rowflagmean_macaw_phys$SWP)^2  #0.068

```
##fruit mask
###merge rowmean with rowmean
```{r}
rowflagmean_macaw_exgexrmask <- aggregate(flagmean_macaw_exgexrmask[,c(4:15,21:32)], by = list("Row"=flagmean_macaw_exgexrmask$Row, "Treatment"=flagmean_macaw_exgexrmask$Treatment, "Block"=flagmean_macaw_exgexrmask$Block, "Date"=flagmean_macaw_exgexrmask$Date), FUN = mean)
dim(rowflagmean_macaw_exgexrmask)  #45,28
dim(rowflagmean_macaw_swp)  #140,5

for(i in 1:dim(rowflagmean_macaw_swp)[1]){
  if(rowflagmean_macaw_swp[i,]$Date=="2019-06-26"){
    rowflagmean_macaw_swp[i,]$Date= "2019-06-28"
  }
  if(rowflagmean_macaw_swp[i,]$Date=="2019-08-01"){
    rowflagmean_macaw_swp[i,]$Date="2019-08-02"
  }
  if(rowflagmean_macaw_swp[i,]$Date=="2019-08-14"){
    rowflagmean_macaw_swp[i,]$Date="2019-08-15"
  }
}

#rowflagmean_macaw_swp$Block <- as.character(rowflagmean_macaw_swp$Block)
rowflagmean_macaw_exgexrmask_swp <- base::merge(rowflagmean_macaw_exgexrmask, rowflagmean_macaw_swp, by = c("Block","Treatment","Date"))
head(rowflagmean_macaw_exgexrmask_swp)
dim(rowflagmean_macaw_exgexrmask_swp)  #45, 30
dim(subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-06-28"))  #15,40
dim(subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-08-02")) #15,40
dim(subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-08-15")) #15, 40


##Change class
rowflagmean_macaw_exgexrmask_swp$Block <- as.factor(rowflagmean_macaw_exgexrmask_swp$Block)
rowflagmean_macaw_exgexrmask_swp$Plot <- as.factor(rowflagmean_macaw_exgexrmask_swp$Plot)

```
####plots
```{r}
a1 = subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-06-28")
a2 = subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-08-02")
a3 = subset(rowflagmean_macaw_exgexrmask_swp, Date=="2019-08-15")
View(a2)
##PRI vs SWP
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri, y = -SWP)) + geom_point() + xlab("PRI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")



cor(rowflagmean_macaw_exgexrmask_swp$pri, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.5479
lm1 <- lm(pri~SWP, data = rowflagmean_macaw_exgexrmask_swp)
summary(lm1)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$pri/rowflagmean_macaw_exgexrmask_swp$ndvi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.537
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/ndvi, y = -SWP)) + geom_point() + xlab("PRI/NDVI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")




##PRI550
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$pri550, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.0004

##PRInorm
###SWP
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$prinorm, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.402


##PRI550norm
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$prinorm550, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.253

##WI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(rowflagmean_macaw_exgexrmask_swp$wi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.541
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
#ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/ndvi, y = -SWP)) + geom_point() + xlab("PRI/NDVI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")


##WI/NDVI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$wi.ndvi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.3886

#Chlorophyll Index
##RER
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$rer, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.00345
##TCARI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$tcari, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.594
##TCARI.OSAVI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$tcari.osavi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.0102
##MCARI

#Strucutre Index
##NDVI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$ndvi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.2751
##RDVI
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$rdvi, rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.5557





##PRI/(RDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")# + xlim(-1.5,0)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")#+xlim(-1.5, 0)
cor(rowflagmean_macaw_exgexrmask_swp$pri/(rowflagmean_macaw_exgexrmask_swp$rdvi*rowflagmean_macaw_exgexrmask_swp$tcari), rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.1052



##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")+facet_wrap(~Date)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$pri/(rowflagmean_macaw_exgexrmask_swp$ndvi*rowflagmean_macaw_exgexrmask_swp$tcari.osavi), rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.591
cor(a1$pri/(a1$ndvi*a1$tcari.osavi), a1$SWP)^2  #0.142
cor(a2$pri/(a2$ndvi*a2$tcari.osavi), a2$SWP)^2  #0.142
cor(a3$pri/(a3$ndvi*a3$tcari.osavi), a3$SWP)^2  #0.142


ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = Treatment)) + xlab("PRI/NDVI*TCARI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")

##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_swp, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_swp$pri/(rowflagmean_macaw_exgexrmask_swp$ndvi*rowflagmean_macaw_exgexrmask_swp$tcari), rowflagmean_macaw_exgexrmask_swp$SWP)^2  #0.3456

```

##plots
```{r}
rowflagmean_macaw_exgexrmask_phys <- aggregate(flagmean_macaw_exgexrmask_phys[,c(8:19, 22:33, 37:40)], by = list("Row"=flagmean_macaw_exgexrmask_phys$Row, "Treatment"=flagmean_macaw_exgexrmask_phys$Treatment, "Block"=flagmean_macaw_exgexrmask_phys$Block, "Date"=flagmean_macaw_exgexrmask_phys$Date), FUN = mean)

rowflagmean_macaw_exgexrmask_phys2 <- subset(rowflagmean_macaw_exgexrmask_phys, Date!="2019-08-15")

##PRI vs SWP
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point() + xlab("PRI from MACAW") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")

##PRI vs Cond
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri, y = Cond)) + geom_point() + xlab("PRI from MACAW") + ylab("Stomatal Conductance") + geom_smooth(method = "lm") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())+facet_wrap(~Date, nrow = 2, scale = "free")


cor(rowflagmean_macaw_exgexrmask_phys$pri, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.554
lm1 <- lm(pri~SWP, data = rowflagmean_macaw_exgexrmask_phys)
summary(lm1)
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Photochemical Reflectance Index (PRI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))


##PRI/NDVI vs SWP
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$pri/rowflagmean_macaw_exgexrmask_phys$ndvi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.543
#The difference is due to the 

##PRI550
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$pri550, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.00879

##PRInorm
###SWP
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$prinorm, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.405
###Cond
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = Cond, color = as.factor(Date))) + geom_point() + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm, y = Cond)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm") + ylab("Cond") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$prinorm, rowflagmean_macaw_exgexrmask_phys$Cond)^2  #0.004


##PRI550norm
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm550, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = prinorm550, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRInorm550") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$prinorm550, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.0788

##WI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("Water Index (WI)") + ylab("SWP (Bars)") + geom_smooth(method = "lm") + theme_bw()+theme(text = element_text(size = 15))
cor(rowflagmean_macaw_exgexrmask_phys$wi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.4004
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = wi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI") + ylab("SWP (Bars)") + geom_smooth(method = "lm", se = FALSE, color = "red") + theme_pubr(border = TRUE, base_size = 14, base_family = "serif", legend = "right")+theme(legend.title = element_blank())


##WI/NDVI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = wi.ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = wi.ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("WI/NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$wi.ndvi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.2169

#Chlorophyll Index
##RER
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = rer, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = rer, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RER") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$rer, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.024
##TCARI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = tcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = tcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$tcari, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.387
##TCARI.OSAVI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = tcari.osavi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = tcari.osavi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("TCARI/OSAVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$tcari.osavi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.3349
##MCARI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = mcari, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = mcari, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("MCARI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$mcari, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.292

#Strucutre Index
##NDVI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = ndvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = ndvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("NDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$ndvi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.1849
##RDVI
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = rdvi, y = -SWP, color = as.factor(Date))) + geom_point() + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = rdvi, y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("RDVI") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$rdvi, rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.324684





##PRI/(RDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(rdvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") + xlim(-1.5,0)
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(rdvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(RDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")+xlim(-1.5, 0)
cor(rowflagmean_macaw_exgexrmask_phys$pri/(rowflagmean_macaw_exgexrmask_phys$rdvi*rowflagmean_macaw_exgexrmask_phys$tcari), rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.068



##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari.osavi), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI/OSAVI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$pri/(rowflagmean_macaw_exgexrmask_phys$ndvi*rowflagmean_macaw_exgexrmask_phys$tcari.osavi), rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.068

##PRI/(NDVI*TCARI)
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari), y = -SWP, color = as.factor(Date))) + geom_point() + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm") 
ggplot(rowflagmean_macaw_exgexrmask_phys, aes(x = pri/(ndvi*tcari), y = -SWP)) + geom_point(aes(color = as.factor(Date))) + xlab("PRI/(NDVI*TCARI)") + ylab("SWP") + geom_smooth(method = "lm")
cor(rowflagmean_macaw_exgexrmask_phys$pri/(rowflagmean_macaw_exgexrmask_phys$ndvi*rowflagmean_macaw_exgexrmask_phys$tcari), rowflagmean_macaw_exgexrmask_phys$SWP)^2  #0.068

```

#Cross comparison
```{r}
dim(rowflagmean_macaw_phys)

phys_weather_PRI <- read.csv(file.path(path_df, "phys_weather_PRI.csv"))
phys_weather_PRI$Date <- as.Date(phys_weather_PRI$Date)
unique(phys_weather_PRI$Date)
for(i in 1:dim(phys_weather_PRI)[1]){
  if(phys_weather_PRI[i,]$Date=="2019-06-25"){
    phys_weather_PRI[i,]$Date = "2019-06-28"
  }
  if(phys_weather_PRI[i,]$Date=="2019-08-01"){
    phys_weather_PRI[i,]$Date = "2019-08-02"
  }
  if(phys_weather_PRI[i,]$Date=="2019-08-14"){
    phys_weather_PRI[i,]$Date = "2019-08-15"
  }
}
names(phys_weather_PRI)[23:25] <- c("Block","Plot","Treatment")
df_PRI_weather_nona <- read.csv(file.path(path_df, "df_PRI_weather_nona.csv"))
names(df_PRI_weather_nona)[3:4] <- c("Block","Treatment")

cross_comp <- merge(rowflagmean_macaw_phys, df_PRI_weather_nona, by = c("Date","Treatment","Block"))
cross_comp2 <- merge(rowflagmean_macaw_phys, phys_weather_PRI, by = c("Date","Treatment","Block"))


dim(cross_comp)
names(cross_comp)
unique(cross_comp$Date)

#pri
ggplot(cross_comp, aes(x = pri, y = PRIm.ma))+geom_point(size = 2,aes(color = as.factor(Date))) + theme_pubr(border = TRUE, legend = "right", base_size = 14, base_family = "serif") + theme(legend.title = element_blank()) + xlab("PRI from UAV") + ylab("PRI from Stand") + xlim(-0.08,0.025) + ylim(-0.08,0.025) + geom_abline(slope = 1, intercept = 0, color = "blue")+geom_smooth(method = "lm", se = FALSE, color = "red")
cor(cross_comp$pri, cross_comp$PRIm.ma)^2
#ndvi
ggplot(cross_comp, aes(x = ndvi, y = NDVIm))+geom_point(size = 2,aes(color = as.factor(Date))) + theme_pubr(border = TRUE, legend = "right", base_size = 14, base_family = "serif") + theme(legend.title = element_blank()) + xlab("NDVI from UAV") + ylab("NDVI from Stand") + xlim(0.65,0.9) + ylim(0.65,0.9)+ geom_abline(slope = 1, intercept = 0, color = "blue")+geom_smooth(method = "lm", se = FALSE, color = "red")
cor(cross_comp$ndvi, cross_comp$NDVIm)^2

ggplot(cross_comp2, aes(x = pri, y = PRIm.ma))+geom_point(aes(color = as.factor(Date)))
cor(cross_comp$pri, cross_comp$PRIm.ma)^2
ggplot(cross_comp2, aes(x = ndvi, y = NDVIm))+geom_point(aes(color = as.factor(Date)))
cor(cross_comp$ndvi, cross_comp$NDVIm)^2

```

#Machine learning 

##Split into Training and Testing 
###Split randomly
```{r}
set.seed(777)
trainIndex <- caret::createDataPartition(flagmean_macaw_phys$SWP, p = 0.7, list = FALSE)
train_PLr <- flagmean_macaw_phys[trainIndex, ]
test_PLr <- flagmean_macaw_phys[-trainIndex,]

#Use the reflectance only
train_PLr_swp1 <- train_PLr[,c(8:19, 23)]
test_PLr_swp1 <- test_PLr[,c(8:19,23)]
names(train_PLr_swp1)
names(test_PLr_swp1)

#Use the index only 
train_PLr_swp2 <- train_PLr[,c(29:31,33,34, 23)]
test_PLr_swp2 <- test_PLr[,c(29:31,33,34,23)]
names(train_PLr_swp2)
names(test_PLr_swp2)

#Use the optimal index 
train_PLr_swp3 <- train_PLr[,c("pri","rdvi","wi","tcari","SWP")]
test_PLr_swp3 <- test_PLr[,c("pri","rdvi","wi","tcari","SWP")]

#Use the optimal index and reflectance only
train_PLr_swp4 <- train_PLr[,c(8:19, 29:31,33,34, 23)]
test_PLr_swp4 <- test_PLr[,c(8:19, 29:31,33,34, 23)]
names(train_PLr_swp4)
```
####random forest regression
#####reflectance only
```{r}
fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
rf_swp1_r <- train(x = train_PLr_swp1[,1:12], y = train_PLr_swp1$SWP, trControl = fitControl, method = "rf", verbose = FALSE, importance = TRUE)
rf_swp1_r
#how accurate the model is 
pred <- predict(rf_swp1_r, newdata = test_PLr_swp1)
cor(pred, test_PLr_swp1$SWP)^2  #0.5469
plot(x=pred, y=test_PLr_swp1$SWP,xlab = c("Predict SWP"), ylab = "Observed SWP", xlim=c(2,10),ylim=c(2,10))+lines(x = c(2,10), y = c(2,10), col = "red")
rmse(pred, test_PLr_swp1$SWP)  #1.343
mae(pred, test_PLr_swp1$SWP)  #1.013

qplot(x=-pred, y=-test_PLr_swp1$SWP,xlab = c("Predicted SWP (Bars)"), ylab = "Observed SWP (Bars)", xlim=c(-2,-10),ylim=c(-2,-10)) + geom_abline(slope = 1, color = "red") + theme_bw()

ggplot(varImp(rf_swp1_r))

sample1 <- shapefile(file.path(path_shp, "sample1.shp"))
macaw_062819_sample1 <- raster::crop(macaw_062819, sample1)
plot(macaw_062819_sample1)
for(i in 1:12){
  macaw_062819_sample1[[i]] <- macaw_062819_sample1[[i]]/65535
}
map_rf_swp1_r_062819 <- predict(object = macaw_062819_sample1, model = rf_swp1_r)
#mask out 
veg_062819_sample1 <- reclassify(macaw_062819_sample1$NDVI, cbind(-Inf, 0.6,NA))
map_rf_swp1_r_062819_masked <- raster::mask(map_rf_swp1_r_062819, veg_062819_sample1)
plot(map_rf_swp1_r_062819_masked, col = brewer.pal(5,"RdYlBu"))
path_output <- "D:/MACAW_tomato/Outputs"
writeRaster(map_rf_swp1_r_062819_masked, file.path(path_output,"map_rf_swp1_r_062819_masked.tif"))

#0802
macaw_080219_sample1 <- raster::crop(macaw_080219, sample1)
for(i in 1:12){
  macaw_080219_sample1[[i]] <- macaw_080219_sample1[[i]]/65535
}
map_rf_swp1_r_080219 <- predict(object = macaw_080219_sample1, model = rf_swp1_r)
#mask out 
veg_080219_sample1 <- reclassify(macaw_080219_sample1$NDVI, cbind(-Inf, 0.6,NA))
map_rf_swp1_r_080219_masked <- raster::mask(map_rf_swp1_r_080219, veg_080219_sample1)
plot(map_rf_swp1_r_080219_masked)
path_output <- "D:/MACAW_tomato/Outputs"
writeRaster(map_rf_swp1_r_080219_masked, file.path(path_output,"map_rf_swp1_r_080219_masked.tif"))

#--------------------------------------

#rf_swp4_r
rf_swp4_r <- train(x = train_PLr_swp4[,1:12], y = train_PLr_swp4$SWP, trControl = fitControl, method = "rf", verbose = FALSE, importance = TRUE)
rf_swp4_r
#how accurate the model is 
pred <- predict(rf_swp4_r, newdata = test_PLr_swp4)
cor(pred, test_PLr_swp4$SWP)^2  #0.5469
plot(x=pred, y=test_PLr_swp4$SWP,xlab = c("Predict SWP"), ylab = "Observed SWP", xlim=c(2,10),ylim=c(2,10))+lines(x = c(2,10), y = c(2,10), col = "red")
rmse(pred, test_PLr_swp4$SWP)  #1.343
mae(pred, test_PLr_swp4$SWP)  #1.013

qplot(x=-pred, y=-test_PLr_swp4$SWP,xlab = c("Predicted SWP (Bars)"), ylab = "Observed SWP (Bars)", xlim=c(-2,-10),ylim=c(-2,-10)) + geom_abline(slope = 1, color = "red") + theme_bw()

ggplot(varImp(rf_swp4_r))


```
#####Optimal index only
```{r}
rf_swp3_r <- train(x = train_PLr_swp3[,1:4], y = train_PLr_swp3$SWP, trControl = fitControl, method = "rf", verbose = FALSE, importance = TRUE)
rf_swp3_r

pred <- predict(rf_swp3_r, newdata = test_PLr_swp3)
cor(pred, test_PLr_swp3$SWP)^2  #0.474
plot(x=pred, y=test_PLr_swp3$SWP,xlab = c("Predict SWP"), ylab = "Observed SWP", xlim=c(2,10),ylim=c(2,10))+lines(x = c(2,10), y = c(2,10), col = "red")
rmse(pred, test_PLr_swp3$SWP)  #1.449
mae(pred, test_PLr_swp3$SWP)  #1.10

ggplot(varImp(rf_swp3_r))
```
####Decision Tree
```{r}
dtree_swp1_r <- train(x = train_PLr_swp1[,1:12], y = train_PLr_swp1$SWP, trControl = fitControl, method = "rpart", tuneLength = 10)
rpart.plot(dtree_swp1_r$finalModel)


pred <- predict(dtree_swp1_r, newdata = test_PLr_swp1)
plot(x = pred, y = test_PLr_swp1$SWP)
```
####xgboost
```{r}
xgb_swp3_r <- train(x = train_PLr_swp3[,1:4], y = train_PLr_swp3$SWP, trControl = fitControl, method = "xgbTree", importance = TRUE)
pred <- predict(xgb_swp3_r, newdata = test_PLr_swp3)
rmse(pred, test_PLr_swp3$SWP)  #1.464
cor(pred, test_PLr_swp3$SWP)^2  #0.464
mae(pred, test_PLr_swp3$SWP)  #1.088
plot(x=pred, y=test_PLr_swp3$SWP,xlab = c("Predict SWP"), ylab = "Observed SWP", xlim=c(2,10),ylim=c(2,10))+lines(x = c(2,10), y = c(2,10), col = "red")
ggplot(varImp(xgb_swp3_r))

rf_swp3_r <- train(x = train_PLr_swp3[,1:4], y = train_PLr_swp3$SWP, trControl = fitControl, method = "rf", verbose = FALSE, importance = TRUE)
rf_swp3_r

pred <- predict(rf_swp3_r, newdata = test_PLr_swp3)
cor(pred, test_PLr_swp3$SWP)^2  #0.474
plot(x=pred, y=test_PLr_swp3$SWP,xlab = c("Predict SWP"), ylab = "Observed SWP", xlim=c(2,10),ylim=c(2,10))+lines(x = c(2,10), y = c(2,10), col = "red")
rmse(pred, test_PLr_swp3$SWP)  #1.449
mae(pred, test_PLr_swp3$SWP)  #1.10

ggplot(varImp(rf_swp3_r))

```



###Split by dates
```{r}
train_PL <- subset(flagmean_macaw_phys, Date!="2019-08-02")
test_PL <- subset(flagmean_macaw_phys, Date=="2019-08-02")

#Use the reflectance only
train_PL_swp1 <- train_PL[,c(8:19, 23)]
test_PL_swp1 <- test_PL[,c(8:19,23)]
names(train_PL_swp1)
names(test_PL_swp1)

#Use the index only 
train_PL_swp2 <- train_PL[,c(29:31,33,34, 23)]
test_PL_swp2 <- test_PL[,c(29:31,33,34,23)]
names(train_PL_swp2)
names(test_PL_swp2)

```

##Random forest regression
###Reflectance only
```{r}
fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
rf_swp1 <- train(x = train_PL_swp1[,1:12], y = train_PL_swp1$SWP, trControl = fitControl, method = "rf", verbose = FALSE)

#how accurate the 
a <- predict(rf_swp1, newdata = test_PL_swp1)
cor(a, test_PL_swp1$SWP)
plot(a, test_PL_swp1$SWP)
```
###Index only
```{r}
rf_swp2 <- train(x = train_PL_swp2[,1:5], y = train_PL_swp2$SWP, trControl = fitControl, method = "rf", verbose = FALSE)

#how accurate the 
a <- predict(rf_swp2, newdata = test_PL_swp2)
cor(a, test_PL_swp2$SWP)

```


```{r}
path_df <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes"
SWP_PL <- read.csv(file.path(path_df, "SWP_Plants.csv"))
head(SWP_PL)
CHL_PL <- read.csv(file.path(path_df, "Chl_Plants.csv"))
tail(CHL_PL)
IRT_PL <- read.csv(file.path(path_df, "IRT_Plants.csv"))
tail(IRT_PL)

unique(SWP_PL$PLOT)
unique(CHL_PL$PLOT)
unique(IRT_PL$PLOT)
dim(SWP_PL)
dim(SWP_PL)

#Row and Block 

```

```{r}
path_phys <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/Physiology"
SWP_BA <- read_excel(file.path(path_phys, "SWP_2019_BlockAve.xlsx"))
NPQ_BA <- read_excel(file.path(path_phys, "NPQ_2019_BlockAve.xlsx"))
LICOR_BA <- read_excel(file.path(path_phys, "LICOR_2019_BlockAve.xlsx"))
FAPAR_BA <- read_excel(file.path(path_phys, "FAPAR_2019_BlockAve.xlsx"))
CHL_BA <- read_excel(file.path(path_phys, "CHL_2019_BlockAve.xlsx"))

#merge them together
phys_BA <- merge(SWP_BA, LICOR_BA, by = c("Date","BLOCK","PLOT","TREATMENT"))
phys_BA <- merge(phys_BA, FAPAR_BA, by = c("Date","BLOCK","PLOT","TREATMENT"))
phys_BA <- merge(phys_BA, CHL_BA, by = c("Date","BLOCK","PLOT","TREATMENT"))
phys_BA <- merge(phys_BA, NPQ_BA, by = c("Date","BLOCK","PLOT","TREATMENT"))
head(phys_BA)
dim(phys_BA)
str(phys_BA)

#change format
phys_BA$Date <- as.Date(phys_BA$Date)
phys_BA$BLOCK <- as.factor(phys_BA$BLOCK)
phys_BA$PLOT <- as.factor(phys_BA$PLOT)
phys_BA$TREATMENT <- as.factor(phys_BA$TREATMENT)

#add ID column
phys_BA$ID <- paste(phys_BA$BLOCK, phys_BA$TREATMENT, sep = " ")

#change date
unique(phys_BA$Date)
unique(flagmean_macaw$Date)

#combine them together
head(flagmean_macaw)
head(phys_BA)
flagmean_macaw_phys <- merge(phys_BA, flagmean_macaw, by = c("Date","Row"))
```
#Use the row average extracted from MACAW
##Read row average
```{r}
path_df <- "C:/Users/tangz/Box Sync/BIOSTIMULANT TRIAL - SEASON 2/ZHEHAN/dataframes"
list.files(path_df)

rowmean_macaw <- read.csv(file.path(path_df, "rowmean_macaw.csv"))
rowmean_macaw_1ft <- read.csv(file.path(path_df, "rowmean_macaw_1ft.csv"))
rowmean_macaw_2ft <- read.csv(file.path(path_df, "rowmean_macaw_2ft.csv"))
rowmean_macaw_3ft <- read.csv(file.path(path_df, "rowmean_macaw_3ft.csv"))

View(rowmean_macaw)
names(rowmean_macaw)

```
##calculate indices
```{r}

```

##Exploratory Plot
```{r}
ggplot(rowmean_macaw, aes(x = Date, y =  ))
```

##Combine with SWP
```{r}
rowmean_macaw_swp <- base::merge(rowmean_macaw, rowflagmean_swp, by = c("Block","Treatment","Date"))

names(rowflagmean_swp)
names(rowmean_macaw) 
```


#---------Useless----------------------------------

##Calculate PRI
```{r}
##raw PRI
rowmean_macaw <- rowmean_macaw %>% mutate(pri = (p530-p570)/(p530+p570))
rowmean_macaw_1ft <- rowmean_macaw_1ft %>% mutate(pri = (p530-p570)/(p530+p570))
rowmean_macaw_2ft <- rowmean_macaw_2ft %>% mutate(pri = (p530-p570)/(p530+p570))
rowmean_macaw_3ft <- rowmean_macaw_3ft %>% mutate(pri = (p530-p570)/(p530+p570))

path_df <- "C:/Users/zt92/Box Sync/BIOSTIMULANT FIELD SCREENING MASTER FOLDER/DRONE/macaw_pri/dataframes"
write.csv(rowmean_macaw, file.path(path_df, "rowmean_macaw.csv"), row.names = FALSE)
write.csv(rowmean_macaw_1ft, file.path(path_df, "rowmean_macaw_1ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_2ft, file.path(path_df, "rowmean_macaw_2ft.csv"), row.names = FALSE)
write.csv(rowmean_macaw_3ft, file.path(path_df, "rowmean_macaw_3ft.csv"), row.names = FALSE)

##corrected PRI
```

#Calculate boxplots 
```{r}
#subset
rowmean_macaw_bayer <- rowmean_macaw[grepl("BAYER", rowmean_macaw$Treatment),]
##dd, ww, ddd
rowmean_macaw_ddd <- rowmean_macaw[grepl("DDD", rowmean_macaw$Treatment),]
rowmean_macaw$DW <- (rowmean_macaw$Treatment)

#0822
temp <- subset(rowmean_macaw_bayer, Date == "2019-08-22")
ggplot(temp, aes(x = Treatment, y = pri, color = Treatment)) + geom_boxplot()+ggtitle("08-22")
#0815
temp <- subset(rowmean_macaw_bayer, Date == "2019-08-15")
ggplot(temp, aes(x = Treatment, y = pri, color = Treatment)) + geom_boxplot()+ggtitle("08-15")

ggplot(rowmean_macaw_bayer, aes(x = Date, y = pri, color = Treatment)) + geom_point()

```

